### 2018-05-07 paper/main.tex
Saving files to github

\documentclass{article}

\usepackage{url}

%\usepackage{nips_2017}
\usepackage[final]{nips_2017}
% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{%
  Kung Faux Pandas \\
  \large Alternative Facts for 
    Privacy Preservation}

%\author{James King \& Seth Russel}
\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V) \\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  \texttt{james.king@ucdenver.edu} \\ 
  \texttt{seth.russell@ucdenver.edu} \\
  }

\date{May 2018}

\begin{document}

% Tell:  articulate the problem with evidence (i.e. papers)
%   Enable reproducibility - patient value, make process of replication easier
%   Time saving
%   legal risk (carrying data in laptops, etc)
%   Multiple comparison?
%   Educational data sets

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

The development and widespread use of literate programming tools such as RMarkdown and Jupyter Notebooks used in conjunction with public code archives like GitLab have enabled a giant leap forward in reproducible research.  It is now possible to write documents which contain source code, visualizations, analytical results, and narrative writing in a single package which can distributed to any interested person for essentially zero cost.

While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the

\bibliographystyle{unsrt}
\bibliography{bib}

\end{document}

### 2018-05-07 paper/autogit.sh
Auto Update from local Sharelatex

@@ -1,0 +1,7 @@
+#!/bin/bash
+cd /home/seth/faker-prototype/paper
+cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
+git pull
+git add *
+git commit -a -m 'Auto Update from local Sharelatex'
+git push

### 2018-05-07 paper/main.tex
Auto Update from local Sharelatex

@@
 \documentclass{article}
-
-\usepackage{url}
 
@@
   James King \& Seth Russell\\
-  Data Science to Patient Value (D2V) \\
+  Data Science to Patient Value (D2V)\\
   School of Medicine \\
   University of Colorado Anschutz Medical Campus\\
+  Aurora, CO\\
   \texttt{james.king@ucdenver.edu} \\ 
@@
 
-% Tell:  articulate the problem with evidence (i.e. papers)
+% Advice from Tell:  articulate the problem with evidence (i.e. papers)
 %   Enable reproducibility - patient value, make process of replication easier
@@
 
+Reproducing Machine learning requires access to source data
+Source data is hard to get
+In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
+Various methods used to synthesize or de-identify
+
+A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
+
 \bibliographystyle{unsrt}

### 2018-05-07 paper/main.tex
Auto Update from local Sharelatex

@@
 While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the 
-
-Reproducing Machine learning requires access to source data
-Source data is hard to get
-In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
-Various methods used to synthesize or de-identify
-
-A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
-
 \bibliographystyle{unsrt}

### 2018-05-07 paper/seth.tex
Auto Update from local Sharelatex

* Reproducing Machine learning requires access to source data
* Source data is hard to get
* In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
* Various methods used to synthesize or de-identify

A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}

### 2018-05-08 paper/seth.tex
Auto Update from local Sharelatex

@@
 A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
+
+Need something smilar to this - part of our 
+"in the U.S., the Privacy Rule of the Health Insurance Portability and Accountability Act (HIPAA)  outlines two policies for protecting anonymity, namely Safe Harbor, and Expert Determination.
+The first of these policies enumerates eighteen direct identifiers that must be removed from data, prior to their dissemi- nation, while, according to the Expert Determination policy, an expert needs to certify that the data to be disseminated pose a low privacy risk before the data can be shared with external parties."

### 2018-05-09 paper/main.tex
Auto Update from local Sharelatex

@@
   University of Colorado Anschutz Medical Campus\\
-  Aurora, CO\\
+%  Aurora, CO\\
   \texttt{james.king@ucdenver.edu} \\ 
@@
 While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the
+
 \bibliographystyle{unsrt}

### 2018-05-09 paper/seth.tex
Auto Update from local Sharelatex

--- 2018-05-07 paper/seth.tex
@@
+"present papers from the coding perspective so that reproducibility and replication of results in the Machine Learning community becomes easier"
+
 * Reproducing Machine learning requires access to source data
@@
 A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
+
+Need something similar to this - part of our motivation for our work:
+"in the U.S., the Privacy Rule of the Health Insurance Portability and Accountability Act (HIPAA)  outlines two policies for protecting anonymity, namely Safe Harbor, and Expert Determination.
+The first of these policies enumerates eighteen direct identifiers that must be removed from data, prior to their dissemination, while, according to the Expert Determination policy, an expert needs to certify that the data to be disseminated pose a low privacy risk before the data can be shared with external parties." (from Publishing data from electronic health records while preserving privacy: A survey of algorithms)
+
+What reference to use for HIPAA? \cite{hippapro}
+
+Need some information (and reference(s)) about IRBs and human subjects research.
+
+Re-identification attacks - should we include brief description about this? Some references: 
+* El Emam K, Jonker E, Arbuckle L, Malin B. A systematic review of re-identification attacks on health data. PLoS ONE 2011;6(12) [e28071, 12].
+* Sweeney L. k-anonymity: a model for protecting privacy. Ijufks 2002;10:557–70.
+
+Reproducing machine learning results in the field of health care is challenging.
+Many published research articles do not make code available nor data available.
+The first issue can be addressed by journal requirements, but the second is much more difficult.
+In the domain of health care in the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act.
+Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (45 CFR 46, Subpart A) and/or the U.S.
+Food and Drug Administration’s regulations (21 CFR 50 and 56).
+Furthermore, the Common Rule established Institutional Review Boards which are responsible and the institutional level of safe guarding human subjects in any research.

### 2018-05-09 paper/main.tex
Auto Update from local Sharelatex

@@
 
-%\usepackage{nips_2017}
-\usepackage[final]{nips_2017}
+\usepackage{nips_2017}
+%\usepackage[final]{nips_2017}
 % to compile a camera-ready version, add the [final] option, e.g.:
@@
 
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=blue,
+}
+
+\urlstyle{same}
 \title{%
@@
 
-%\author{James King \& Seth Russel}
+%\author{Seth Russel  \& James King}
 \author{
@@
 %  Aurora, CO\\
+  \texttt{seth.russell@ucdenver.edu} \\
   \texttt{james.king@ucdenver.edu} \\ 
-  \texttt{seth.russell@ucdenver.edu} \\
   }
@@
 \begin{abstract}
+A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing.
 
@@
 
-The development and widespread use of literate programming tools such as RMarkdown and Jupyter Notebooks used in conjunction with public code archives like GitLab have enabled a giant leap forward in reproducible research.
-It is now possible to write documents which contain source code, visualizations, analytical results, and narrative writing in a single package which can distributed to any interested person for essentially zero cost.
+Reproducing machine learning results in the field of health care is challenging.
+Many published research articles do not make code nor data available.
+Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law \cite{hippapro}.
 
-While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the
+\section{Appendix: Legal References}
+In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).
+
+Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (\href{https://www.hhs.gov/ohrp/regulations-and-policy/regulations/45-cfr-46/index.html#subparta}{45 CFR 46, Subpart A}) and/or the U.S.
+Food and Drug Administration’s regulations (\href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.50&rgn=div5}{21 CFR 50} and \href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.56&rgn=div5}{56}).
+Furthermore, the Common Rule established Institutional Review Boards which are responsible and the institutional level of safe guarding human subjects in any research.
 

### 2018-05-09 paper/seth.tex
Auto Update from local Sharelatex

@@
 Reproducing machine learning results in the field of health care is challenging.
-Many published research articles do not make code available nor data available.
-The first issue can be addressed by journal requirements, but the second is much more difficult.
-In the domain of health care in the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act.
+Many published research articles do not make code nor data available.
+Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law.
+
+ In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act.
 Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (45 CFR 46, Subpart A) and/or the U.S.

### 2018-05-09 paper/seth.tex
Auto Update from local Sharelatex

@@
 
-* Reproducing Machine learning requires access to source data
-* Source data is hard to get
-* In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
-* Various methods used to synthesize or de-identify
-
-A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
-
-Need something similar to this - part of our motivation for our work:
-"in the U.S., the Privacy Rule of the Health Insurance Portability and Accountability Act (HIPAA)  outlines two policies for protecting anonymity, namely Safe Harbor, and Expert Determination.
-The first of these policies enumerates eighteen direct identifiers that must be removed from data, prior to their dissemination, while, according to the Expert Determination policy, an expert needs to certify that the data to be disseminated pose a low privacy risk before the data can be shared with external parties." (from Publishing data from electronic health records while preserving privacy: A survey of algorithms)
-
-What reference to use for HIPAA? \cite{hippapro}
-
-Need some information (and reference(s)) about IRBs and human subjects research.
+Need some information (and reference(s)) about IRBs and human subjects research?
 
@@
 
+\section{Introduction}
+
 Reproducing machine learning results in the field of health care is challenging.
-Many published research articles do not make code nor data available.
-Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law.
+Historically, many published research articles do not make code nor data available which limits the ability of other researchers to validate or reproduce results.
+While some high impact journals such as the Nature Research journal family have adopted policies to promote software and data sharing \cite{natmethods}, not all journals and locations where machine learning methods are published have such policies.
+Despite a growing trend toward code and data sharing policies, there are additional difficulties in sharing health care data due to legal requirements.
 
- In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act.
+ In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (HIPAA) \cite{hippapro}.
 Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (45 CFR 46, Subpart A) and/or the U.S.
 Food and Drug Administration’s regulations (21 CFR 50 and 56).
-Furthermore, the Common Rule established Institutional Review Boards which are responsible and the institutional level of safe guarding human subjects in any research.
+Furthermore, the Common Rule established Institutional Review Boards which are responsible and the institutional level of safe guarding human subjects in any research; similar layers of laws and legal controls exist in other countries.
+Due to the many constraints in place, even appropriate and routine requests to access data can take a significant amount of effort and time.
+Importantly, only the approved group or individual can access data; it cannot be shared in original form or used for other purposes, so secondary, educational or other key data use cases are left unmet.
+
+ As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (?
+cite recent non-reproducible examples such as Google FHIR, others?).
+In order to resolve the problem of data sharing, various methods for data synthesis and de-identification have been developed in other data domains that have been applied to health care.
+The use of privacy preserving techniques as methods to safely share health care or other data have a history of re-identification risk as detailed by Sweeney \cite{sweeney_2002}.
+Alternative techniques of synthetic data have been used to avoid the potential problem of re-identification.
+One early example by Gray et al.
+\cite{gray_quickly_1994} used pseudo-random generation techniques to populate large databases with synthetic data for performance evaluation.
+Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates and entire outpatient Electronic Health Record (EHR) based on population statistics.
+
+ While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
+Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in and actual EHR due to rare or complex conditions.
+Other techniques based on actual health data such as described by Gal et al.
+\cite{gal_data_2014} provide for the complexities found in real health data by building off of the condensation algorithm \cite{aggarwal_static_2008} though use of k-means clustering, Principle Component Analysis, and independent data generation pipelines based on a specific outcome variable.
+While the method as depicted by Gal results in a use case specific synthetic data set, the manual intervention required to develop a synthetic data requires an ongoing effort between the data source and researchers needing access to data.
+In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.

### 2018-05-09 paper/main.tex
Auto Update from local Sharelatex

@@
 
-\usepackage{nips_2017}
-%\usepackage[final]{nips_2017}
+%\usepackage{nips_2017}
+\usepackage[final]{nips_2017}
 % to compile a camera-ready version, add the [final] option, e.g.:
@@
 %   Educational data sets
+%  Definition of :reproducibility 
+%       reproducibilty - everything same - code, data, result
+%       replicability - code same, new data, same result find Peng & Leek reference (also look at blog)
+%   unit testing...
 
@@
 \begin{abstract}
-A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing.
+A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.
 
@@
 Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law \cite{hippapro}.
+
+Various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
+Broadly speaking, these methods fall into two categories: anonymization and synthesis.
+Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data
 

### 2018-05-09 paper/seth.tex
Auto Update from local Sharelatex

@@
 \cite{gray_quickly_1994} used pseudo-random generation techniques to populate large databases with synthetic data for performance evaluation.
-Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates and entire outpatient Electronic Health Record (EHR) based on population statistics.
+Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates an entire outpatient Electronic Health Record (EHR) based on population statistics.
 
  While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
-Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in and actual EHR due to rare or complex conditions.
+Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in an actual EHR due to rare or complex conditions.
 Other techniques based on actual health data such as described by Gal et al.

### 2018-05-09 __init__.py
First commit

@@ -1,0 +1,41 @@
+###########################################################################
+#
+###########################################################################
+#
+#
+#     _______         .-''-.
+#     \  ___ `'.    .' .-.  ).----.     .----.
+#      ' |--.\  \  / .'  / /  \    \   /    /
+#      | |    \  '(_/   / /    '   '. /'   /
+#      | |     |  '    / /     |    |'    /
+#      | |     |  |   / /      |    ||    |
+#      | |     ' .'  . '       '.   `'   .'
+#      | |___.' /'  / /    _.-')\        /
+#     /_______.'/ .' '  _.'.-''  \      /
+#     \_______|/ /  /.-'_.'       '----'
+#               /    _.'
+#              ( _.-'
+#     ___             __     __  _           _____
+#    / _ | ___  ___ _/ /_ __/ /_(_)______   / ___/__  _______
+#   / __ |/ _ \/ _ `/ / // / __/ / __(_-<  / /__/ _ \/ __/ -_)
+#  /_/ |_/_//_/\_,_/_/\_, /\__/_/\__/___/  \___/\___/_/  \__/
+#                    /___/
+#
+#
+# by The Data Science to Patient Value (D2V) Analytics Core,
+#      University of Colorado School of Medicine
+#
+###############################################################################
+#
+###############################################################################
+
+
+import mysql.connector as mariadb
+mariadb_connection = mariadb.connect(user='python_user', password='some_pass', database='employees')
+cursor = mariadb_connection.cursor()
+
+def __init__(self):
+
+    self.request_query = ''
+
+

### 2018-05-09 fakelite3.py

@@ -1,0 +1,104 @@
+
+import sqlite3
+import pandas as pd
+import numpy as np
+from numpy.random import choice
+import scipy as sp
+import scipy.stats as stats
+import pylab as plt
+from collections import Counter
+
+
+
+class KungFauxPanda():
+
+    # To do:  Check to see if a column is unique (i.e. index) and recreate with unique < maybe use sample without replacement?>
+
+    def __init__(self, density_depth='column', verbose=True):
+
+        self.verbose = verbose
+        self.seed = 102935104
+        self.density_depth = density_depth # ('column', 'table', 'join')
+        # if # of unique values is small compared to number of records,
+        # assume it's a factor
+        self.determine_factors = True
+        self.factor_threshold = 0.15
+
+    def read_sql(self, sql, conn):
+
+        self.sql = sql
+        self.conn = conn
+        self.df = pd.read_sql(self.sql, self.conn)
+
+        if self.density_depth == 'column':
+            self.column_kde()
+            return self.fdf
+
+        elif self.type == 'KDE':
+            #d0 = df.iloc[:,[0,1,2,3,4]].transpose()
+            kd = stats.gaussian_kde(self.df, bw_method='silverman')
+            dnew = dict(zip(self.df.columns, kd.resample()))
+
+
+    def column_kde(self):
+        out_dict = dict()
+
+        for col in self.df.columns:
+            thistype = self.df[col].dtype
+
+            if len(set(self.df[col]))/len(self.df[col]) < self.factor_threshold and self.determine_factors:
+                thistype = 'object'
+
+            if thistype == 'int64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df[col], bw_method='silverman')
+                out_dict[col] = np.int64(kd.resample().ravel())
+
+            elif thistype =='float64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df[col], bw_method='silverman')
+                out_dict[col] = kd.resample().ravel()
+
+            else:
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+
+                colfact = self.df[col].factorize()
+                cc=Counter(colfact[0])
+
[…]

### 2018-05-09 mariapdb.py

@@ -1,0 +1,12 @@
+
+
+
+import mysql.connector as mariadb
+
+class pseudocursor(mysql.connector.cursor))
+    # Overload all methods which return data
+:
+
+def main():
+    mariadb_connection = mariadb.connect(user='python_user', password='some_pass', database='employees')
+    cursor = mariadb_connection.cursor()

### 2018-05-10 paper/seth.tex
Auto Update from local Sharelatex

@@
 In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.
+
+ \section{Reproducibility}
+ %Good discussion of what reproducibilty vs replicability means
+ %http://languagelog.ldc.upenn.edu/nll/?p=21956
+ To clarify what we mean by reproducibility in machine learning, a brief discussion of what the term reproducibility
+ Over the past 15 years or so, there has been some significant papers clarifying the definition and importance of reproducibility, along with the closely related term replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experi- ment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}.
+One early influential paper on the topic of reproducibility in scientifici computing by Schwab details key factors in reproducbility as: having data, input parameters, documenation, software code, and an environment capable of running the provided software code \cite{schwab_making_2000}.

### 2018-05-10 paper/seth.tex
Auto Update from local Sharelatex

--- 2018-05-09 paper/seth.tex
@@
 In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.
+
+ \section{Reproducibility}
+ %Good discussion of what reproducibilty vs replicability means
+ %http://languagelog.ldc.upenn.edu/nll/?p=21956
+ Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
+Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
+One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducbility as having: data, input parameters, documenation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
+Reproducibility should be treated as a minimium required standard that all published research should meet \cite{peng_reproducible_2006}.
+Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article.
+Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.

### 2018-05-14 paper/main.tex
Auto Update from local Sharelatex

@@
   Kung Faux Pandas \\
-  \large Alternative Facts for 
-    Privacy Preservation}
+  \large A tool for enabling data sharing in health care}
 
@@
 
+\section{Background}
+
+ Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
+Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
+One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducbility as having: data, input parameters, documenation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
+Reproducibility should be treated as a minimium required standard that all published research should meet \cite{peng_reproducible_2006}.
+Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article.
+Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
+
 \section{Appendix: Legal References}

### 2018-05-14 paper/main.tex
Auto Update from local Sharelatex

@@
 
+\usepackage{soul}           % added by seth - remove before submission, provides highlighting support
+
 \usepackage{hyperref}
@@
 
-%\author{Seth Russel  \& James King}
 \author{
@@
   University of Colorado Anschutz Medical Campus\\
-%  Aurora, CO\\
+  Aurora, CO\\
+  \texttt{james.king@ucdenver.edu} \\
   \texttt{seth.russell@ucdenver.edu} \\
-  \texttt{james.king@ucdenver.edu} \\ 
   }
@@
 \begin{abstract}
-A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.
+\hl{to finish:} A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.
 
@@
 
+The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
+Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.
+
 \section{Background}
@@
 
+As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (?
+cite recent difficult to reproduce examples such as Google FHIR paper, others?).
+In order to resolve the problem of data sharing, various methods for data synthesis and de-identification have been developed in other data domains that have been applied to health care.
+The use of privacy preserving techniques as methods to safely share health care or other data have a history of re-identification risk as detailed by Sweeney \cite{sweeney_2002}.
+Alternative techniques of synthetic data have been used to avoid the potential problem of re-identification.
+One early example by Gray et al.
+\cite{gray_quickly_1994} used pseudo-random generation techniques to populate large databases with synthetic data for performance evaluation.
+Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates an entire outpatient Electronic Health Record (EHR) based on population statistics.
+
+While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
+Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in an actual EHR due to rare or complex conditions.
+Other techniques based on actual health data such as described by Gal et al.
+\cite{gal_data_2014} provide for the complexities found in real health data by building off of the condensation algorithm \cite{aggarwal_static_2008} though use of k-means clustering, Principle Component Analysis, and independent data generation pipelines based on a specific outcome variable.
+While the method as depicted by Gal results in a use case specific synthetic data set, the manual intervention required to develop a synthetic data requires an ongoing effort between the data source and researchers needing access to data.
+In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.
+
+\section{Methods}
+
+? James write this section ?
+
+\section{Conclusion}
+
+Basically need to put abstract here...
+
 \section{Appendix: Legal References}
+
+\hl{Where to put this? Probably don't want to waste any of our 4 pages with an appendix... Include this in body or not at all?}
+
 In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).

### 2018-05-14 paper/main.tex
Auto Update from local Sharelatex

@@
 %   unit testing...
+%   Proof of privacy guarantees?
 
@@
 Reproducing machine learning results in the field of health care is challenging.
-Many published research articles do not make code nor data available.
-Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law \cite{hippapro}.
+Many published research articles do not make code nor data available which limits the ability of others to reproduce results.
+While journals could require the inclusion of code and data in submissions, there are legal restrictions that prevent the sharing of data in the health care domain \cite{hippapro}.
 
-Various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
+There are various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
 Broadly speaking, these methods fall into two categories: anonymization and synthesis.
-Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data
+Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data is generalized so distributed data cannot be tied to a single individual.
+Synthetic methods generate data based on algorithms, publicly known disease models, or other sources not specific to an individual.
 
-The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
+The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.
+The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
 Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.
@@
 Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducbility as having: data, input parameters, documenation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
-Reproducibility should be treated as a minimium required standard that all published research should meet \cite{peng_reproducible_2006}.
+One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
+Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
 Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
@@
 
-? James write this section ?
+Describe why selected Pandas for extension; synthesis method...
 

### 2018-05-18 paper/main.tex

@@
 \usepackage{microtype}      % microtypography
+\usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing
 
@@
 
+\makeatletter
+
+\newenvironment{chapquote}[2][2em]
+  {\setlength{\@tempdima}{#1}%
+   \def\chapquote@author{#2}%
+   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
+   \itshape}
+  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
+\makeatother
+
 \maketitle
@@
 
-The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.
-The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
+The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux-data creation from user generated queries.
+The faux-data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
 Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.
@@
 
+\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
+``Because it works, bitches.''
+\end{chapquote}
+
+The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
+Unfortunately, the mechanisms of populating the scientific literature were designed on \nth{17} century assumptions which are inadequate for some modern scientific endeavors such as machine learning.
+
+Though there are semantic variations in the use of the words "replicate," "reproduce," etc., most commentaries on the subject agree that an independent experiment with confirmatory results is the strongest support of any experiment \cite{leek_opinion_2015, drummond_replicability_2009}.
+In the machine learning context, the ability to independently arrive at similar results from similar data requires the documentation of many technical (and frankly, banal) parameters which is rarely done within published papers.
+Many of these, such as the versions used of various software libraries, can be captured in virtual environments, but parameters related to the data are often much trickier to capture, particularly if the data used in an analysis is sensitive and cannot be shared.
+
+\subsection{Seth's Original}
 Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.

### 2018-05-18 mariapdb.py
Synching up

@@ -1,12 +1,0 @@
-
-
-
-import mysql.connector as mariadb
-
-class pseudocursor(mysql.connector.cursor))
-    # Overload all methods which return data
-:
-
-def main():
-    mariadb_connection = mariadb.connect(user='python_user', password='some_pass', database='employees')
-    cursor = mariadb_connection.cursor()

### 2018-05-18 sourcecode/html/js/site.js
Saving updates to environment build scripts; adding functionality to web UI and REST services

@@ -1,6 +1,11 @@
 /*
 Custom javascript stuff goes here
 */
+
+//Need to configure port for AJAX calls. Default is port 8000 on same host as html
+var HOST = window.location.hostname;
+var PORT = '8000';
+
 $('#query_results').on('hidden.bs.collapse', function () {
   console.log('caught hidden event');
   $('#qr_indicator').removeClass('fa-minus');
@@ -27,23 +32,70 @@ $('#metadata').on('shown.bs.collapse', function () {
 
 $('#submit').click(function() {
   console.log('Called submit click.')
-  // need to make ajax call with this text:
-  console.log(editor.getValue());
+
+  var jqxhr = $.ajax({
+    dataType: 'json',
+    type: 'GET',
+    url: 'http://' + HOST + ':' + PORT + '/synthesize_data',
+    data: {
+      query: editor.getValue(),
+      method: 'kde'
+    }
+  })
+    .done(function(data) {
+      // need to add elements to query result area...
+      // create columns
+      // populate rows
+      console.log(jqxhr);
+      console.log(data);
+    })
+    .fail(function(jqXHR, textStatus, errorThrown) {
+      console.log('error encountered attempting to get synthetic data');
+    });
+
 })
 
 $('#reset').click(function() {
   editor.setValue(editor_default_text);
   editor.focus(); //To focus the ace editor
-  var n = editor.getSession().getValue().split("\n").length; // To count total no. of lines
+  var n = editor.getSession().getValue().split('\n').length; // To count total no. of lines
   editor.gotoLine(n); //Go to end of document
 })
 
-var editor = ace.edit("editor");
+var editor = ace.edit('editor');
 var editor_default_text = '-- Type SQL Code here\n';
-editor.setTheme("ace/theme/crimson_editor");
-editor.session.setMode("ace/mode/sql");
+editor.setTheme('ace/theme/crimson_editor');
+editor.session.setMode('ace/mode/sql');
 
 editor.setOptions({
-  fontSize: "13px"
+  fontSize: '13px'
 });
 $('#reset').click();
+
+// Assign handlers immediately after making the request,
+// and remember the jqXHR object for this request
+var jqxhr = $.ajax({
+  dataType: 'json',
+  url: 'http://' + HOST + ':' + PORT + '/synthesis_methods'})
+  .done(function(data) {
+    // need to add elements to UI...
+    console.log(jqxhr);
+    console.log(data);
+    if (data.response.constructor === Array) {
+      data.response.forEach(function(m, index){
[…]

### 2018-05-18 sourcecode/python/web-service.py

@@ -1,12 +1,29 @@
 import hug
+from fakelite3 import KungFauxPandas
+import sqlite3
 
+kfpd = KungFauxPandas()
+dbname = '../../data/sepsis.db'
+db_conn = sqlite3.connect(dbname)
 
-@hug.get(examples='query=select')
+@hug.response_middleware()
+def process_data(request, response, resource):
+      response.set_header('Access-Control-Allow-Origin', '*')
+
+@hug.get(examples='query=select * from table&method=kde')
 @hug.local()
-def generate_data(query: hug.types.text):
+def synthesize_data(query: hug.types.text, method: hug.types.text):
     """Does nothing right now"""
     response = 'No data found'
+    df = kfpd.read_sql(query, db_conn, method)
     return {
         'message': 'need to provide message here',
         'query': '{0}'.format(query),
-        'response': response}
+        'response': df.to_json()}
+
+@hug.get()
+@hug.local()
+def synthesis_methods():
+    return {
+        'message': 'available data synthesis methods',
+        'response': kfpd.synthesis_methods}

### 2018-05-26 sourcecode/scripts/docker_startup.sh
Tweaks to docker scripts

@@ -7,7 +7,17 @@ cd ../python
 
 #tail -f /app/web_service.log
 
-while :; do
-  sleep 100
-  echo -n "."
+cleanup ()
+{
+kill -s SIGTERM $!
+exit 0
+}
+
+trap cleanup SIGINT SIGTERM
+
+while [ 1 ]
+do
+    echo -n "."
+    sleep 10 &
+    wait $!
 done

### 2018-05-26 sourcecode/scripts/docker_startup.sh
Using a virtualenv reduces image size

@@ -1,4 +1,8 @@
 #! /bin/bash
+
+cd ../python
+source kungfauxpandas/bin/activate
+
 cd ../html
 python -m http.server 8080 >> /app/http_server.log 2>&1
 

### 2018-05-26 sourcecode/scripts/docker_startup.sh
Forgot to fix path to hug

@@ -7,7 +7,7 @@ cd ../html
 python -m http.server 8080 >> /app/http_server.log 2>&1
 
 cd ../python
-/usr/local/bin/hug -p 8000 -f web-service.py >> /app/web_service.log 2>&1
+hug -p 8000 -f web-service.py >> /app/web_service.log 2>&1
 
 #tail -f /app/web_service.log
 

### 2018-05-27 sourcecode/scripts/docker_startup.sh
More testing/tweaking

@@ -1,7 +1,8 @@
 #! /bin/bash
 
-cd ../python
-source kungfauxpandas/bin/activate
+pwd
+
+env
 
 cd ../html
 python -m http.server 8080 >> /app/http_server.log 2>&1

### 2018-05-28 sourcecode/python/old_fakelite3.py
Realized I never committed the old testing version of the fakifier; updating scripts to match

@@ -1,0 +1,98 @@
+
+import sqlite3
+import pandas as pd
+import numpy as np
+from numpy.random import choice
+import scipy.stats as stats
+from collections import Counter
+
+class KungFauxPandas():
+
+    # To do:  Check to see if a column is unique (i.e. index) and recreate with unique < maybe use sample without replacement?>
+
+    def __init__(self, density_depth='column', verbose=True):
+
+        self.verbose = verbose
+        self.seed = 102935104
+        self.density_depth = density_depth # ('column', 'table', 'join')
+        # if # of unique values is small compared to number of records,
+        # assume it's a factor
+        self.determine_factors = True
+        self.factor_threshold = 0.15
+        self.synthesis_methods = ('sgf', 'kde', 'datasynthesizer')
+
+    def read_sql(self, sql, conn, method_type):
+        self.sql = sql
+        self.conn = conn
+        self.df = pd.read_sql(self.sql, self.conn)
+
+        if self.density_depth == 'column':
+            self.column_kde()
+            return self.fdf
+
+        elif self.type == 'KDE':
+            #d0 = df.iloc[:,[0,1,2,3,4]].transpose()
+            kd = stats.gaussian_kde(self.df, bw_method='silverman')
+            dnew = dict(zip(self.df.columns, kd.resample()))
+
+
+    def column_kde(self):
+        out_dict = dict()
+
+        for col in self.df.columns:
+            thistype = self.df[col].dtype
+
+            if len(set(self.df[col]))/len(self.df[col]) < self.factor_threshold and self.determine_factors:
+                thistype = 'object'
+
+            if thistype == 'int64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df[col], bw_method='silverman')
+                out_dict[col] = np.int64(kd.resample().ravel())
+
+            elif thistype =='float64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df[col], bw_method='silverman')
+                out_dict[col] = kd.resample().ravel()
+
+            else:
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+
+                colfact = self.df[col].factorize()
+                cc=Counter(colfact[0])
+
[…]

### 2018-05-28 sourcecode/python/web-service.py

@@ -1,5 +1,5 @@
 import hug
-from seth_fakelite3 import KungFauxPandas
+from old_fakelite3 import KungFauxPandas
 import sqlite3
 import sys
 import re

### 2018-05-28 sourcecode/scripts/docker_startup.sh

@@ -1,9 +1,4 @@
 #! /bin/bash
-
-pwd
-
-env
-
 cd ../html
 python -m http.server 8080 >> /app/http_server.log 2>&1
 

### 2018-05-28 sourcecode/scripts/docker_startup.sh
Saving updates

@@ -1,9 +1,9 @@
 #! /bin/bash
 cd ../html
-python -m http.server 8080 >> /app/http_server.log 2>&1
+python -m http.server 8080 >> /app/http_server.log 2>&1 &
 
 cd ../python
-hug -p 8000 -f web-service.py >> /app/web_service.log 2>&1
+hug -p 8000 -f web-service.py >> /app/web_service.log 2>&1 &
 
 #tail -f /app/web_service.log
 

### 2018-05-29 sourcecode/html/js/site.js
Integrating with the new kungfauxpandas classes; update to readme about docker

@@ -140,7 +140,7 @@ $( document ).ready(function() {
             console.log(m);
           var html_to_append = '<div class="form-check form-check-inline"><input class="form-check-input" type="radio" name="selected_method" id="'
           html_to_append += 'selected_method' + index + '"';
-          if (m === 'kde')
+          if (m === 'KDE')
             html_to_append += 'value="' + m + '" checked>';
           else {
             html_to_append += 'value="' + m + '">';

### 2018-05-29 sourcecode/python/kungfauxpandas.py

@@ -3,11 +3,13 @@ import pandas as pd
 import numpy as np
 import scipy.stats as stats
 import sys
+import warnings
 
-library_location = '../../plugins/DataSynthesizer/DataSynthesizer'
+library_location = '../../plugins/DataSynthesizer'
 sys.path.append(library_location)
 
 from DataSynthesizer.DataDescriber import DataDescriber
+
 ####################################################################################################################################
 ####################################################################################################################################
 
@@ -35,11 +37,10 @@ class TrivialPlugin(PandaPlugin):
 
 
     def fauxify(self, df_in=None):
-        if df_in:
+        if df_in is not None:
             self.df_in = df_in
-        else:
-            self.df_out = self.df_in
 
+        self.df_out = self.df_in
 
         return self.df_out
 
@@ -47,7 +48,7 @@ class TrivialPlugin(PandaPlugin):
 class DataSynthesizerPlugin(PandaPlugin):
     """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
 
-    def __init__(self, df_in,
+    def __init__(self, df_in=None,
             mode = 'correlated_attribute_mode',
             threshold_value = 0.1,
             categorical_attributes = {},
@@ -58,8 +59,6 @@ class DataSynthesizerPlugin(PandaPlugin):
 
         PandaPlugin.__init__(self)
 
-        self.library_location = '../../plugins/DataSynthesizer/DataSynthesizer'
-        sys.path.append(self.library_location)
         self.mode = mode
 
         # An attribute is categorical if its domain size is less than this threshold.
@@ -81,7 +80,7 @@ class DataSynthesizerPlugin(PandaPlugin):
 
         # The maximum number of parents in Bayesian network, i.e., the maximum number of incoming edges.
         # self.degree_of_bayesian_network = 2
-        self.degree_of_bayesian_network = degree_of_baysian_network
+        self.degree_of_bayesian_network = degree_of_bayesian_network
 
         # Number of tuples generated in synthetic dataset.
         # self.num_tuples_to_generate = 10000 # Can be set to any integer.
@@ -97,23 +96,23 @@ class DataSynthesizerPlugin(PandaPlugin):
         from DataSynthesizer.DataGenerator import DataGenerator
         from DataSynthesizer.ModelInspector import ModelInspector
         from DataSynthesizer.lib.utils import read_json_file, display_bayesian_network
-        import warnings
 
-        if df_in == None:
+        if df_in is None:
[…]

### 2018-05-29 sourcecode/python/web-service.py

@@ -1,5 +1,5 @@
 import hug
-from old_fakelite3 import KungFauxPandas
+from kungfauxpandas import KungFauxPandas, TrivialPlugin, DataSynthesizerPlugin, KDEPlugin
 import sqlite3
 import sys
 import re
@@ -64,7 +64,13 @@ def synthesize_data(query: hug.types.text, method: hug.types.text):
                 fixed_query += '\norder by random()'
 
         try:
-            df = kfpd.read_sql(fixed_query, db_conn, method)
+            if method is not None:
+                for m in kfpd.synthesis_methods:
+                    if method.lower() == m.lower():
+                        method = m
+                print(globals()[method + 'Plugin'])
+
+            df = kfpd.read_sql(fixed_query, db_conn)
 
             # if any order by clauses were present, re-apply them
             if len(order_clauses) > 0:

### 2018-05-29 paper/main.tex
Auto Update from local Sharelatex

--- 2018-05-14 paper/main.tex
@@
   Kung Faux Pandas \\
-  \large A tool for enabling data sharing in health care}
+  \large Alternative Facts for Privacy Protection}
 
@@
 %   unit testing...
+%   Proof of privacy guarantees?
+
+\makeatletter
+
+\newenvironment{chapquote}[2][2em]
+  {\setlength{\@tempdima}{#1}%
+   \def\chapquote@author{#2}%
+   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
+   \itshape}
+  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
+\makeatother
 
@@
 
-Reproducing machine learning results in the field of health care is challenging.
-Many published research articles do not make code nor data available.
-Journals could require the inclusion of code in submissions, however most health care data is very strictly protected by law \cite{hippapro}.
+%Reproducing machine learning results in the field of health care is challenging.
+Many published research articles do not make code nor data available which limits the ability of others to reproduce results.
+While journals could require the inclusion of code and data in submissions, there are legal restrictions that prevent the sharing of data in the health care domain \cite{hippapro}.
 
-Various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
+%There are various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
 Broadly speaking, these methods fall into two categories: anonymization and synthesis.
-Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data
+Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data is generalized so distributed data cannot be tied to a single individual.
+Synthetic methods generate data based on algorithms, publicly known disease models, or other sources not specific to an individual.
 
-The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
+%The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux-data creation from user generated queries.
+The faux-data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
 Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.
+
+\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
+``Because it works, bitches.''
+\end{chapquote}
+
+The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
+Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate enabling reproducibility for some modern scientific endeavors such as machine learning.
+Perhaps the most important impediment to reproducibility is the need to share data.
+This has long been difficult in health care fields, but will presently become difficult for just about everyone.
+
+There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{<give the bigguns>}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+
+This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which integrates \emph{any} of these data security methods into the popular Python Pandas data science library.
+For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.
 
@@
 
-Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
+Machine Learning (ML) methods are perhaps the most difficult to make ``reproducible'' in any sense of the term.
+This difficulty has many sources:  a quickly evolving set of software tools with various levels of compatibility, a need for massive computational infrstructure, the ``black magic'' methods for building the model structures, and intense apetite for training data.
+Huge piles of training data.
+
+So in order to reproduce a model, one needs a full set of library metadata, an impossibly expensive computer, model metadata which is nearly impossible to replicate by a description, and a large data set that the original researchers are not likely to give you.
+
+The first few of those obstacles are technological in nature and can be overcome by some subtle alterations in the ``scientific machine'' and improvements to computing.
+That last problem, though, is HUGE.
+A reproducer needs appropriate data, even to simply veryify that a trained model actually works as described.
+Setting aside the natural tendency of scientists to dislike sharing data out of fear of being scooped, there are ominous legal constraints on data sharing which will most likely become more intense over time.
+
+At the writing of this paper, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cided>}, extending the preeminance of data privacy over data sharing to all fields in that jurisdiction.
+In fact, the GDPR enables the data owner (i.e.
+the person about whom the data is collected) has the ability to revoke permission to use the data at any time.
+Most other countries will likely implement similar legislation in the near future \cite{?}.
+
+Thus, without signifcant technological and policy infrastructure, it's essentially illegal to share data about humans.
+By extension, it's difficult if not outright illegal to attempt to reproduce the results of a machine learning model created by an outside entity.
+
+%Though there are semantic variations in the use of the words "replicate," "reproduce," etc., most commentaries on the subject agree that an independent experiment with confirmatory results is the strongest support of any experiment \cite{leek_opinion_2015, drummond_replicability_2009}.
+In the machine learning context, the ability to independently arrive at similar results from similar data requires the documentation of many technical (and frankly, banal) parameters which is rarely done within published papers.
+Many of these, such as the versions used of various software libraries, can be captured in virtual environments, but parameters related to the data are often much trickier to capture, particularly if the data used in an analysis is sensitive and cannot be shared.
+
+%\subsection{Seth's Original}
+%Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
 Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
 Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducbility as having: data, input parameters, documenation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
-Reproducibility should be treated as a minimium required standard that all published research should meet \cite{peng_reproducible_2006}.
+One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
+Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
 Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
@@
 
-As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (?
+%As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (?
 cite recent difficult to reproduce examples such as Google FHIR paper, others?).
@@
 
-While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
+%While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
 Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in an actual EHR due to rare or complex conditions.
@@
 
-? James write this section ?
+Describe some popular approaches to anonymization and sysnthesis
+
+Describe KFP's structure, including the ``plugin'' mechanism.
+
+Describe the SQL interface
 
@@
 
-\section{Appendix: Legal References}
+%\section{Appendix: Legal References}
 
-\hl{Where to put this? Probably don't want to waste any of our 4 pages with an appendix... Include this in body or not at all?}
+%\hl{Where to put this? Probably don't want to waste any of our 4 pages with an appendix... Include this in body or not at all?}
 
-In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).
+% I vote not at all
 
-Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (\href{https://www.hhs.gov/ohrp/regulations-and-policy/regulations/45-cfr-46/index.html#subparta}{45 CFR 46, Subpart A}) and/or the U.S.
+%In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).
+
+%Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (\href{https://www.hhs.gov/ohrp/regulations-and-policy/regulations/45-cfr-46/index.html#subparta}{45 CFR 46, Subpart A}) and/or the U.S.
 Food and Drug Administration’s regulations (\href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.50&rgn=div5}{21 CFR 50} and \href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.56&rgn=div5}{56}).

### 2018-05-29 paper/autogit.sh

@@ -1,5 +1,5 @@
 #!/bin/bash
-cd /home/seth/faker-prototype/paper
+cd /home/seth/kungfauxpandas/paper
 cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
 git pull
 git add *

### 2018-05-29 paper/autogit.sh
Auto Update from local Sharelatex

@@ -3,5 +3,5 @@ cd /home/seth/kungfauxpandas/paper
 cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
 git pull
 git add *
-git commit -a -m 'Auto Update from local Sharelatex'
+git commit -a -m 'Auto Update from local Sharelatex'  --author="magic-lantern <magic-lantern@users.noreply.github.com>"
 git push

### 2018-05-29 sourcecode/html/js/site.js
Fixing plugin method selection

@@ -58,7 +58,7 @@ $('#submit').click(function() {
     url: 'http://' + HOST + ':' + PORT + '/synthesize_data',
     data: {
       query: editor.getValue(),
-      method: 'kde'
+      method: $('input[name=selected_method]:checked').val()
     }
   })
     .done(function(data) {

### 2018-05-29 sourcecode/python/kungfauxpandas.py

@@ -143,7 +143,7 @@ class KDEPlugin(PandaPlugin):
 
     def fauxify(self, df_in=None, *args, **kwargs):
 
-        self.df = df_in
+        self.df_in = df_in
 
         self.factor_threshold = 0.15 # if > this % are unique, assume it's NOT a factor
         self.determine_factors = True

### 2018-05-29 sourcecode/python/web-service.py

@@ -67,9 +67,7 @@ def synthesize_data(query: hug.types.text, method: hug.types.text):
             if method is not None:
                 for m in kfpd.synthesis_methods:
                     if method.lower() == m.lower():
-                        method = m
-                print(globals()[method + 'Plugin'])
-
+                        kfpd.plugin = globals()[m + 'Plugin']()
             df = kfpd.read_sql(fixed_query, db_conn)
 
             # if any order by clauses were present, re-apply them

### 2018-05-30 sourcecode/python/kungfauxpandas.py
Adding ability to pass additional arguments to be interpreted by pandas read_sql

@@ -227,12 +227,11 @@ class KungFauxPandas(object):
         self.synthesis_methods = ('Trivial', 'KDE', 'DataSynthesizer')
 
     #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-    def read_sql(self, sql, conn):
+    def read_sql(self, sql, conn, **kwargs):
 
         self.sql = sql
         self.conn = conn
-        self.df_in = pd.read_sql(self.sql, self.conn)
-
+        self.df_in = pd.read_sql(self.sql, self.conn, **kwargs)
         self.df_out = self.plugin.fauxify(self.df_in)
         return self.df_out
         '''

### 2018-05-30 sourcecode/python/kungfauxpandas.py
Modifications to get DataSynthesizer working - correlated mode doesn't work, so switched to independent mode

@@ -18,7 +18,7 @@ class PandaPlugin(object):
     def __init__(self, df_in = None):
         self.df_in = df_in
 
-    def fauxify(self, df_in=None):
+    def fauxify(self, df_in=None, **kwargs):
         """All plugins need to overload this fauxify method which takes a pandas data frame
         and returns a faux-data data frame."""
 
@@ -49,13 +49,14 @@ class DataSynthesizerPlugin(PandaPlugin):
     """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
 
     def __init__(self, df_in=None,
-            mode = 'correlated_attribute_mode',
-            threshold_value = 0.1,
+            mode = 'independent_attribute_mode',
+            threshold_value = 20,
             categorical_attributes = {},
             candidate_keys = {},
             epsilon = 0.1,
             degree_of_bayesian_network = 2,
-            num_tuples_to_generate = 1000):
+            num_tuples_to_generate = None,
+            save_faux_data_to_file = False):
 
         PandaPlugin.__init__(self)
 
@@ -69,24 +70,26 @@ class DataSynthesizerPlugin(PandaPlugin):
         #self.categorical_attributes = {'education': True}
         self.categorical_attributes = categorical_attributes
 
-        # specify which attributes are candidate keys of input dataset.
+        # specify which attributes are candidate keys (or not keys) for input dataset.
         #self.candidate_keys = {'ssn': True}
+        #self.candidate_keys = {'age': False}
         self.candidate_keys = candidate_keys
 
-        # A parameter in differential privacy.
-        # It roughtly means that removing one tuple will change the probability of any output by  at most exp(epsilon).
-        # Set epsilon=0 to turn off differential privacy.
-        self.epsilon = epsilon
+        if mode == "correlated_attribute_mode":
+            # A parameter in differential privacy.
+            # It roughtly means that removing one tuple will change the probability of any output by  at most exp(epsilon).
+            # Set epsilon=0 to turn off differential privacy.
+            self.epsilon = epsilon
 
-        # The maximum number of parents in Bayesian network, i.e., the maximum number of incoming edges.
-        # self.degree_of_bayesian_network = 2
-        self.degree_of_bayesian_network = degree_of_bayesian_network
+            # The maximum number of parents in Bayesian network, i.e., the maximum number of incoming edges.
+            # self.degree_of_bayesian_network = 2
+            self.degree_of_bayesian_network = degree_of_bayesian_network
 
         # Number of tuples generated in synthetic dataset.
[…]

### 2018-05-30 paper/main.tex
Auto Update from local Sharelatex
First save of decomposed plugins--not working yet

--- 2018-05-14 paper/main.tex
@@
 \usepackage{microtype}      % microtypography
+\usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing
 
+\usepackage{graphicx}       % added by seth - image support
+\graphicspath{ {./images/} }
 \usepackage{soul}           % added by seth - remove before submission, provides highlighting support
@@
 \begin{abstract}
-\hl{to finish:} A description of an end-to-end system for easily generating synthetic data which contains no Personal Health Information (PHI), allowing example data to be distributed for reproducibility testing and other purposes.
-
+A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.
+This system makes enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
 \end{abstract}
@@
 
-Reproducing machine learning results in the field of health care is challenging.
-Many published research articles do not make code nor data available which limits the ability of others to reproduce results.
-While journals could require the inclusion of code and data in submissions, there are legal restrictions that prevent the sharing of data in the health care domain \cite{hippapro}.
+\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
+``Because it works, bitches.''
+\end{chapquote}
 
-There are various approaches to building data sets which simultaneously have scientific utility and comply with privacy laws.
-Broadly speaking, these methods fall into two categories: anonymization and synthesis.
-Anonymization methods attempt to keep as much of the "real" data as possible, whilst ensuring that person-specific data is generalized so distributed data cannot be tied to a single individual.
-Synthetic methods generate data based on algorithms, publicly known disease models, or other sources not specific to an individual.
+The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
+Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate enabling reproducibility for some modern scientific endeavors such as machine learning.
+Perhaps the most important impediment to reproducibility is the need to share data.
+This has long been difficult in health care fields, but will presently become difficult for just about everyone.
 
-The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries.
-The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI).
-Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.
+There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{	patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+
+This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which integrates \emph{any} of these data security methods into the popular Python Pandas data science library.
+For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.
 
@@
 
-Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
-Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
-Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}.
-Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
-Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
-The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article.
-Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
+In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.
+Thus, even institutitions which which to share data face a steep institutional risk.
+This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.
 
-As machine learning results are highly data dependent, the barriers around sharing health data make it difficult or impossible for others to verify or reproduce results with novel machine learning methods in the health care domain (?
-cite recent difficult to reproduce examples such as Google FHIR paper, others?).
-In order to resolve the problem of data sharing, various methods for data synthesis and de-identification have been developed in other data domains that have been applied to health care.
-The use of privacy preserving techniques as methods to safely share health care or other data have a history of re-identification risk as detailed by Sweeney \cite{sweeney_2002}.
-Alternative techniques of synthetic data have been used to avoid the potential problem of re-identification.
-One early example by Gray et al.
-\cite{gray_quickly_1994} used pseudo-random generation techniques to populate large databases with synthetic data for performance evaluation.
-Subsequent advances in techniques have generated more realistic data based on observed and publicly reported statistics, such as with the Synthea system \cite{walonoski_synthea:_2018}, that generates an entire outpatient Electronic Health Record (EHR) based on population statistics.
+Perhaps more ominously for researchers, on \hl{May 25 , 2018}, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
+In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
 
-While advances in both de-identification and synthesis of data have been impressive, still more progress needs to be made.
-Techniques such as Synthea that generate an entire EHR require significant computational power and model development of every disease state desired and may not have the level of specificity as found in an actual EHR due to rare or complex conditions.
-Other techniques based on actual health data such as described by Gal et al.
-\cite{gal_data_2014} provide for the complexities found in real health data by building off of the condensation algorithm \cite{aggarwal_static_2008} though use of k-means clustering, Principle Component Analysis, and independent data generation pipelines based on a specific outcome variable.
-While the method as depicted by Gal results in a use case specific synthetic data set, the manual intervention required to develop a synthetic data requires an ongoing effort between the data source and researchers needing access to data.
-In this paper we propose a method that allows the user of the data to identify what attributes they are interested in, does not require manual intervention or generation of synthetic data, and is modular so that as new techniques are developed the system could be updated to take advantage of them.
+These rules are ultimately good for citizens, but they create a pickle for scientists studying humans as it's very difficult to follow normal processes in scientific rigor while complying with privacy protection rules.
+
+One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.
+This is fairly straight-forward to implement.
+Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.
+The custodian then runs it and returns the results to the researcher.
+
+This has been technologically possible for some time, but it's awkward in practice because activities such as data cleaning, exploration, and plotting are interactive and iterative processes which would become impractical with a mediator.
+
+Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+
+This faux-data can be prodded, poked, plotted, and posted for the world to see, enabling analysts to develop their code using whatever means they prefer.
+When the analytical code is ready, it can then be sent to the data custodian to run on the real data.
 
@@
 
-Describe why selected Pandas for extension; synthesis method...
+Many methods of generating the faux-data exist in the literature, many of which have software implementations freely available.
+KFP provides a standard mechanism for ``wrapping'' any method into a ``plug-in'' which integrates the method with the Pandas data frame model.
+Three of these plug-ins are provided with full documentation for creating other plug-ins.
+
+\subsection{Included Methods}
+
+\begin{tabular}{c c c p{10em}}
+
+Method & Source & Plug-In Name & Notes \\ 
+\hline
+
+Kernel Density Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\
+
+DataSynthesizer &  <authors> & DataSynthesizerPlugin & Generates a Baysean tree to capture some column relationships \\
+
+\hl{CMF?}  & <authors>  & Can't Remember & Fast \\
+
+\hline 
+\end{tabular}
+
+Describe KFP's structure, including the ``plugin'' mechanism.
+
+Describe the SQL interface
+
+Diagrams - not sure if we need both of these. Should we include a screenshot of the UI (saved to /images)?
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{prototype_architecture}
+  \caption{System Architecture.}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{data_synthesis_process}
+  \caption{Data synthesis process.}
+\end{figure}
 
@@
 
-\section{Appendix: Legal References}
+\bibliographystyle{unsrt}
 
-\hl{Where to put this? Probably don't want to waste any of our 4 pages with an appendix... Include this in body or not at all?}
-
-In the U.S., the primary law affecting health data privacy is the Health Insurance Portability and Accountability Act (\href{https://www.hhs.gov/hipaa/for-professionals/index.html}{HIPAA}).
-
-Additionally, organizations desiring to perform biomedical and social, behavioral, and educational research are subject to Common Rule (\href{https://www.hhs.gov/ohrp/regulations-and-policy/regulations/45-cfr-46/index.html#subparta}{45 CFR 46, Subpart A}) and/or the U.S.
-Food and Drug Administration’s regulations (\href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.50&rgn=div5}{21 CFR 50} and \href{https://www.ecfr.gov/cgi-bin/text-idx?SID=faa4b2b2900a70fbcac4a773c9da0f0f&mc=true&node=pt21.1.56&rgn=div5}{56}).
-Furthermore, the Common Rule established Institutional Review Boards which are responsible and the institutional level of safe guarding human subjects in any research.
-
-\bibliographystyle{unsrt}
 \bibliography{bib}

### 2018-05-30 sourcecode/python/KungFauxPandas/DataSynthesizerPlugin.py

@@ -1,0 +1,143 @@
+
+import pandas as pd
+import numpy as np
+import scipy.stats as stats
+import sys
+import warnings
+
+try:
+    library_location = '../../plugins/DataSynthesizer'
+    sys.path.append(library_location)
+    from DataSynthesizer.DataDescriber import DataDescriber
+
+except Exception as e:
+    warnings.warn('DataSynthesizer source code appears to be absent.  This module will not function')
+
+
+from KungFauxPandas import PandaPlugin
+
+
+####################################################################################################################################
+####################################################################################################################################
+
+class DataSynthesizerPlugin(PandaPlugin):
+    """ uses methods from <authors>'s Data Synthsizer to fauxify data """
+
+    def __init__(self, df_in=None,
+            mode = 'correlated_attribute_mode',
+            threshold_value = 0.1,
+            categorical_attributes = {},
+            candidate_keys = {},
+            epsilon = 0.1,
+            degree_of_bayesian_network = 2,
+            num_tuples_to_generate = 1000):
+
+        PandaPlugin.__init__(self)
+
+        self.mode = mode
+
+        # An attribute is categorical if its domain size is less than this threshold.
+        #self.threshold_value = 20
+        self.threshold_value = threshold_value
+
+        # specify categorical attributes
+        #self.categorical_attributes = {'education': True}
+        self.categorical_attributes = categorical_attributes
+
+        # specify which attributes are candidate keys of input dataset.
+        #self.candidate_keys = {'ssn': True}
+        self.candidate_keys = candidate_keys
+
+        # A parameter in differential privacy.
+        # It roughtly means that removing one tuple will change the probability of any output by  at most exp(epsilon).
+        # Set epsilon=0 to turn off differential privacy.
+        self.epsilon = epsilon
+
+        # The maximum number of parents in Bayesian network, i.e., the maximum number of incoming edges.
+        # self.degree_of_bayesian_network = 2
+        self.degree_of_bayesian_network = degree_of_bayesian_network
+
+        # Number of tuples generated in synthetic dataset.
+        # self.num_tuples_to_generate = 10000 # Can be set to any integer.
+        self.num_tuples_to_generate = num_tuples_to_generate# Can be set to any integer.
+
+
+
+    #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+    def fauxify(self, df_in=None, *args, **kwargs):
+
[…]

### 2018-05-30 sourcecode/python/KungFauxPandas/KDEPlugin.py

@@ -1,0 +1,95 @@
+
+####################################################################################################################################
+####################################################################################################################################
+
+#from KungFauxPandas import *
+from KungFauxPandas import PandaPlugin 
+
+class KDEPlugin(PandaPlugin):
+    """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
+    
+    import pandas as pd
+    import numpy as np
+    import scipy.stats as stats
+    import sys
+    import warnings
+
+
+    def __init__(self, verbose=True):
+        self.verbose = verbose
+        PandaPlugin.__init__(self)
+
+    #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+    def fauxify(self, df_in=None, *args, **kwargs):
+
+        self.df_in = df_in
+
+        self.factor_threshold = 0.15 # if > this % are unique, assume it's NOT a factor
+        self.determine_factors = True
+
+        for key, value in kwargs.items():
+
+            if key == "factor_threshold":
+                self.factor_threshold = value
+
+            elif key == "determine_factors":
+                self.determine_factors = True
+
+            else:
+                if self.verbose:
+                    warnings.warn('Keyword argument', key, 'not used')
+
+        # sets self.df_out
+        self.column_kde()
+
+        return self.df_out
+
+    #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+    def column_kde(self):
+
+        from numpy.random import choice
+        from collections import Counter
+
+        out_dict = dict()
+
+        for col in self.df_in.columns:
+            thistype = self.df_in[col].dtype
+
+            if len(set(self.df_in[col]))/len(self.df_in[col]) < self.factor_threshold and self.determine_factors:
+                thistype = 'object'
+
+            if thistype == 'int64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df_in[col], bw_method='silverman')
+                out_dict[col] = np.int64(kd.resample().ravel())
+
+            elif thistype =='float64':
+                if self.verbose:
+                    print('Processing column ' + col + ' as a ' + str(thistype))
+                kd = stats.gaussian_kde(self.df_in[col], bw_method='silverman')
+                out_dict[col] = kd.resample().ravel()
+
+            else:
+                if self.verbose:
[…]

### 2018-05-30 sourcecode/python/KungFauxPandas/PandaPlugin.py

@@ -1,0 +1,17 @@
+
+####################################################################################################################################
+####################################################################################################################################
+
+class PandaPlugin(object):
+
+    def __init__(self, df_in = None):
+        self.df_in = df_in
+
+    def fauxify(self, df_in=None):
+        """All plugins need to overload this fauxify method which takes a pandas data frame
+        and returns a faux-data data frame."""
+
+        print('This is a template--use it to make a plugin')
+
+
+####################################################################################################################################

### 2018-05-30 sourcecode/python/KungFauxPandas/TrivialPlugin.py

@@ -1,0 +1,29 @@
+
+####################################################################################################################################
+####################################################################################################################################
+
+from KungFauxPandas import PandaPlugin 
+
+class TrivialPlugin(PandaPlugin):
+    """ Returns the input as output. 
+	
+	Shows a basic example to build your own plugin"""
+
+    def __init__(self):
+        PandaPlugin.__init__(self)
+
+
+    def fauxify(self, df_in=None):
+        if df_in is not None:
+            self.df_in = df_in
+
+
+	# To make this non-trivial, do something cool and save the results as self.df_out
+	#
+	# self.df_out = coolstuff.something_cool(df_in)
+
+        self.df_out = self.df_in
+
+        return self.df_out
+
+####################################################################################################################################

### 2018-05-30 sourcecode/python/KungFauxPandas/__init__.py

@@ -29,13 +29,6 @@
 #
 ###############################################################################
 
+__all__=['PandaPlugin','TrivialPlugin','KDEPlugin','DataSynthesizerPlugin', 'faux_read_sql']
 
-import mysql.connector as mariadb
-mariadb_connection = mariadb.connect(user='python_user', password='some_pass', database='employees')
-cursor = mariadb_connection.cursor()
-
-def __init__(self):
-
-    self.request_query = ''
-
-
+#from KungFauxPandas import *

### 2018-05-30 sourcecode/python/KungFauxPandas/faux_read_sql.py

@@ -1,0 +1,30 @@
+
+
+####################################################################################################################################
+####################################################################################################################################
+
+
+# To do:  Check to see if a column is unique (i.e. index) and recreate with unique < maybe use sample without replacement?>
+
+#def __init__(self, plugin=TrivialPlugin, verbose=True):
+#    self.verbose = verbose
+#    self.seed = 10293510
+#    self.plugin = plugin
+#    self.synthesis_methods = ('Trivial', 'KDE', 'DataSynthesizer')
+
+#- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+#from KungFauxPandas import *
+
+def faux_read_sql( sql, con, plugin=TrivialPlugin, index_col=None, coerce_float=True, params=None, parse_dates=None, columns=None, chunksize=None):
+    
+
+    import pandas as pd
+    
+    self.sql = sql
+    self.con = con
+    self.df_in = pd.read_sql(sql, con, index_col, coerce_float, params, parse_dates, columns, chunksize)
+    self.df_out = self.plugin.fauxify(self.df_in)
+
+    return self.df_out
+
+####################################################################################################################################

### 2018-05-30 sourcecode/python/KungFauxPandas/kungfauxpandas.py

@@ -1,0 +1,32 @@
+
+import pandas
+import numpy as np
+import scipy.stats as stats
+import sys
+import warnings
+import TrivialPlugin
+
+####################################################################################################################################
+####################################################################################################################################
+
+class kungfauxpandas():
+
+    # To do:  Check to see if a column is unique (i.e. index) and recreate with unique < maybe use sample without replacement?>
+
+    def __init__(self, plugin=TrivialPlugin, verbose=True):
+        self.verbose = verbose
+        self.seed = 10293510
+        self.plugin = plugin
+        self.synthesis_methods = ('Trivial', 'KDE', 'DataSynthesizer')
+
+    #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+    def read_sql(sql, con, index_col=None, coerce_float=True, params=None,
+             parse_dates=None, columns=None, chunksize=None):
+ 
+        self.sql = sql
+        self.con = con
+        self.df_in = pd.read_sql(sql, con, index_col, coerce_float, params, parse_dates, columns, chunksize)
+        self.df_out = self.plugin.fauxify(self.df_in)
+        return self.df_out
+
+####################################################################################################################################

### 2018-05-30 sourcecode/python/kungfauxpandas.py

@@ -1,312 +1,0 @@
-
-import pandas as pd
-import numpy as np
-import scipy.stats as stats
-import sys
-import warnings
-
-library_location = '../../plugins/DataSynthesizer'
-sys.path.append(library_location)
-
-from DataSynthesizer.DataDescriber import DataDescriber
-
-####################################################################################################################################
-####################################################################################################################################
-
-class PandaPlugin(object):
-
-    def __init__(self, df_in = None):
-        self.df_in = df_in
-
-    def fauxify(self, df_in=None):
-        """All plugins need to overload this fauxify method which takes a pandas data frame
-        and returns a faux-data data frame."""
-
-        print('This is a template--use it to make a plugin')
-
-
-####################################################################################################################################
-####################################################################################################################################
-
-class TrivialPlugin(PandaPlugin):
-    """ Returns the input as output. """
-
-    def __init__(self):
-        PandaPlugin.__init__(self)
-
-
-
-    def fauxify(self, df_in=None):
-        if df_in is not None:
-            self.df_in = df_in
-
-        self.df_out = self.df_in
-
-        return self.df_out
-
-
-class DataSynthesizerPlugin(PandaPlugin):
-    """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
-
-    def __init__(self, df_in=None,
-            mode = 'correlated_attribute_mode',
-            threshold_value = 0.1,
-            categorical_attributes = {},
-            candidate_keys = {},
-            epsilon = 0.1,
-            degree_of_bayesian_network = 2,
-            num_tuples_to_generate = 1000):
-
-        PandaPlugin.__init__(self)
-
-        self.mode = mode
-
-        # An attribute is categorical if its domain size is less than this threshold.
-        #self.threshold_value = 20
-        self.threshold_value = threshold_value
-
-        # specify categorical attributes
-        #self.categorical_attributes = {'education': True}
-        self.categorical_attributes = categorical_attributes
-
-        # specify which attributes are candidate keys of input dataset.
-        #self.candidate_keys = {'ssn': True}
-        self.candidate_keys = candidate_keys
-
-        # A parameter in differential privacy.
-        # It roughtly means that removing one tuple will change the probability of any output by  at most exp(epsilon).
-        # Set epsilon=0 to turn off differential privacy.
[…]

### 2018-05-30 paper/main.tex
Auto Update from local Sharelatex

@@
 \author{
-  James King \& Seth Russell\\
+  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
   Data Science to Patient Value (D2V)\\
@@
   Aurora, CO\\
-  \texttt{james.king@ucdenver.edu} \\
-  \texttt{seth.russell@ucdenver.edu} \\
+  \texttt{james.king@ucdenver.edu}, \texttt{seth.russell@ucdenver.edu},\\ \texttt{tell.bennett@ucdenver.edu} \texttt{debashis.ghosh@ucdenver.edu}
   }
@@
 
-\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
-``Because it works, bitches.''
-\end{chapquote}
-
 The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
@@
 In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.
-Thus, even institutitions which which to share data face a steep institutional risk.
+Thus, even institutions which share data face a steep institutional risk.
 This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.
 
-Perhaps more ominously for researchers, on \hl{May 25 , 2018}, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
+Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
 In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
@@
 
-\section{Methods}
+\section{System Details}
 
@@
 \end{tabular}
+
+\subsection{System Structure}
+KFP provides a class
 

### 2018-05-31 paper/nips_2018.tex
Recent update to workshop says to use NIPS 2018 LaTeX styles

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2018

% ready for submission
\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
% \usepackage[preprint]{nips_2018}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2018}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2018}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting instructions for NIPS 2018}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2018}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2018/}
\end{center}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2018 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. Additional pages \emph{containing only
  acknowledgments and/or cited references} are allowed. Papers that
exceed eight pages of content (ignoring references) will not be
reviewed, or in any other way considered for presentation at the
conference.

The margins in 2018 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2018.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2018 is \verb+nips_2018.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+,
which creates a camera-ready copy, \verb+preprint+, which creates a
preprint for submission to, e.g., arXiv, and \verb+nonatbib+, which will
not load the \verb+natbib+ package for you in case of package clash.

\paragraph{New preprint option for 2018}
If you wish to post a preprint of your work online, e.g., on arXiv,
using the NIPS style, please use the \verb+preprint+ option. This will
create a nonanonymized version of your work with the text
``Preprint. Work in progress.''  in the footer. This version may be
distributed as you see fit. Please \textbf{do not} use the
\verb+final+ option, which should \textbf{only} be used for papers
accepted to NIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper
as they will be removed during generation of camera-ready copies.

The file \verb+nips_2018.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2018+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2018}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can use more than eight pages as long as the
  additional pages contain \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

@@
 
-%\usepackage{nips_2017}
-\usepackage[final]{nips_2017}
+% if you need to pass options to natbib, use, e.g.:
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2018
+
+% ready for submission
+%\usepackage{nips_2018}
+
+% to compile a preprint version, e.g., for submission to arXiv, add
+% add the [preprint] option:
+\usepackage[preprint]{nips_2018}
+
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
+% \usepackage[final]{nips_2018}
+
+% to avoid loading the natbib package, add option nonatbib:
+% \usepackage[nonatbib]{nips_2018}
 
@@
   Data Science to Patient Value (D2V)\\
-  School of Medicine \\
+  School of Medicine\\
   University of Colorado Anschutz Medical Campus\\
   Aurora, CO\\
-  \texttt{james.king@ucdenver.edu}, \texttt{seth.russell@ucdenver.edu},\\ \texttt{tell.bennett@ucdenver.edu} \texttt{debashis.ghosh@ucdenver.edu}
+  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
   }
@@
 A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.
-This system makes enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
+This system, which is publicly available \footnote{\url{https://github.com/CUD2V/kungfauxpandas}}, enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
 \end{abstract}
@@
 
-There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{	patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
 

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

@@
 
-\makeatletter
-
-\newenvironment{chapquote}[2][2em]
-  {\setlength{\@tempdima}{#1}%
-   \def\chapquote@author{#2}%
-   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
-   \itshape}
-  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
-\makeatother
-
 \maketitle
@@
 
-Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
+Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
 In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
@@
 
-Kernel Density Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\
+Kernel Density\\Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\
 
-DataSynthesizer &  <authors> & DataSynthesizerPlugin & Generates a Baysean tree to capture some column relationships \\
+DataSynthesizer & Ping et al. & DataSynthesizerPlugin & Generates a Bayesian tree to capture column relationships \\
 
-\hl{CMF?}  & <authors>  & Can't Remember & Fast \\
+Synthetic dataset\\Generation Framework & Bindschaedler et al.  & SGFPlugin & Fast \\
 

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

@@
 
-\begin{tabular}{c c c p{10em}}
+Some text about Table~\ref{included-methods}
 
-Method & Source & Plug-In Name & Notes \\ 
-\hline
-
-Kernel Density\\Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\
-
-DataSynthesizer & Ping et al. & DataSynthesizerPlugin & Generates a Bayesian tree to capture column relationships \\
-
-Synthetic dataset\\Generation Framework & Bindschaedler et al.  & SGFPlugin & Fast \\
-
-\hline 
+\begin{table}
+  \caption{Kung Faux Pandas data synthesis methods}
+  \label{included-methods}
+  \centering
+  \begin{tabular}{p{12em} l p{14em}}
+    \toprule
+    Method                                 & Source                    & Notes \\
+    \midrule
+    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
+    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
+    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
+    \bottomrule
   \end{tabular}
+\end{table}
 
@@
 
-\begin{figure}[h]
+The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
+However, as discussed previously, legal limitations and data protection processes are slow.
+Figure ~\ref{fig:architecture}
+
+\begin{figure}[ht]
   \centering
@@
   \caption{System Architecture.}
+  \label{fig:architecture}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[ht]
   \centering
-  \includegraphics[width=\textwidth]{data_synthesis_process}
+  \includegraphics[width=115mm]{data_synthesis_process}
   \caption{Data synthesis process.}
+  \label{fig:synthesis_process}
 \end{figure}

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

@@
 \usepackage{soul}           % added by seth - remove before submission, provides highlighting support
+\usepackage{wrapfig}        % added by seth for placing images in-line with text
 
@@
 
-This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which integrates \emph{any} of these data security methods into the popular Python Pandas data science library.
+% explain faux here? faux data - similar to faux fur or faux leather - ethically more appealing, less expensive to produce or use
+This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular use of data security methods into the popular Python Pandas data science library.
 For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.
@@
 
-Many methods of generating the faux-data exist in the literature, many of which have software implementations freely available.
+Many methods of generating faux-data exist in the literature, many of which have software implementations freely available.
 KFP provides a standard mechanism for ``wrapping'' any method into a ``plug-in'' which integrates the method with the Pandas data frame model.
@@
 However, as discussed previously, legal limitations and data protection processes are slow.
-Figure ~\ref{fig:architecture}
+Figure ~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
 
@@
 \end{figure}
+
+\begin{wrapfigure}[15]{r}{0.5\textwidth} %this figure will be at the right
+  \centering
+  \includegraphics[width=0.5\textwidth]{ui_screenshot2}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{wrapfigure}
+
+KFP provides multiple methods by which a machine learning developer could request on-demand synthetic data.
+A web we currently have a web based user interface and a REST interface that takes a SQL query, executes it, runs the data through a synthesis process Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

--- 2018-05-31 paper/main.tex
@@
 
-Some text about Table~\ref{included-methods}
+Some text about Table~\ref{included-methods}% Not sure where this table should go....
 
@@
 
-Diagrams - not sure if we need both of these. Should we include a screenshot of the UI (saved to /images)?
-
 The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
 However, as discussed previously, legal limitations and data protection processes are slow.
-Figure ~\ref{fig:architecture}
+Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
 
@@
 
+Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux data request/response process.
+All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process; "ORDER BY" clauses are re-applied to the faux data before results are returned to the user.
+All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries.
+Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
+While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
+Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
+
 \begin{figure}[ht]
   \centering
-  \includegraphics[width=115mm]{data_synthesis_process}
+  \includegraphics[width=120mm]{data_synthesis_process}
   \caption{Data synthesis process.}
@@
 \end{figure}
+
+\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+  \centering
+  \includegraphics[width=0.5\textwidth]{ui_screenshot2}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{wrapfigure}
+KFP provides multiple methods by which a machine learning developer can access on-demand synthetic data.
+Multiple methods of requesting and receiving faux data are provided.
+As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected synthesis method.
+Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
+Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
+Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
 

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

@@
 
+% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
+
 Many methods of generating faux-data exist in the literature, many of which have software implementations freely available.
@@
 Three of these plug-ins are provided with full documentation for creating other plug-ins.
+
+\subsection{System Structure}
+KFP provides a class
+
+Describe KFP's structure, including the ``plugin'' mechanism.
+
+Describe the SQL interface
+
+The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
+However, as discussed previously, legal limitations and data protection processes are slow.
+Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{prototype_architecture}
+  \caption{System Architecture.}
+  \label{fig:architecture}
+\end{figure}
+
+Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux data request/response process.
+All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
+All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries.
+Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
+While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
+Previously removed "ORDER BY" clauses are re-applied to the faux data before results are returned to the user.
+Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
+
+Query pre-processor and synthesis process could optionally require a minimu source data size...
+
+%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
+%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
+%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
+%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=120mm]{data_synthesis_process}
+  \caption{Data synthesis process.}
+  \label{fig:synthesis_process}
+\end{figure}
+
+% figure out how to adjust padding
+\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+  \centering
+  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{wrapfigure}
+KFP provides multiple methods by which a machine learning developer can access on-demand synthetic data.
+Multiple methods of requesting and receiving faux data are provided.
+As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected synthesis method.
+Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
+Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
+Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
 
@@
 
-\subsection{System Structure}
-KFP provides a class
-
-Describe KFP's structure, including the ``plugin'' mechanism.
-
-Describe the SQL interface
-
-The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
-However, as discussed previously, legal limitations and data protection processes are slow.
-Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{prototype_architecture}
-  \caption{System Architecture.}
-  \label{fig:architecture}
-\end{figure}
-
-Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux data request/response process.
-All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process; "ORDER BY" clauses are re-applied to the faux data before results are returned to the user.
-All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries.
-Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
-While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
-Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=120mm]{data_synthesis_process}
-  \caption{Data synthesis process.}
-  \label{fig:synthesis_process}
-\end{figure}
-
-\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
-  \centering
-  \includegraphics[width=0.5\textwidth]{ui_screenshot2}
-  \caption{User Interface.}
-  \label{fig:ui}
-\end{wrapfigure}
-KFP provides multiple methods by which a machine learning developer can access on-demand synthetic data.
-Multiple methods of requesting and receiving faux data are provided.
-As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected synthesis method.
-Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
-Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
-Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
-
 \section{Conclusion}

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

@@
   Kung Faux Pandas \\
-  \large Alternative Facts for Privacy Protection}
+  \large Alternative Facts for Privacy Protection %Simplifying Privacy Protection?
+  }
 
@@
 
-Some text about Table~\ref{included-methods}% Not sure where this table should go....
+Some text about Table~\ref{included-methods} including why we built the KDE method, why DataSynthesizer, and why SGF% Not sure where this table should go....
 
@@
 
+\section{Discussion}
+
+Limitations, areas for further research:
+
+\begin{itemize}
+    \item Python module
+    \item Currently don't impose any kind of result set minimum size
+    \item Use in production
+\end{itemize}
+
 \section{Conclusion}

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

@@
   Kung Faux Pandas \\
-  \large Alternative Facts for Privacy Protection %Simplifying Privacy Protection?
+  \large Simplifying Privacy Protection
   }
@@
 % explain faux here? faux data - similar to faux fur or faux leather - ethically more appealing, less expensive to produce or use
+% faux data is a broader term that encompasses any data privacy protection method - synthesis, anonymization, grouping, perturbation, etc.
 This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular use of data security methods into the popular Python Pandas data science library.
@@
 
-Query pre-processor and synthesis process could optionally require a minimu source data size...
-
-%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
-%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
-%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
-%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
-
 \begin{figure}[ht]
@@
 \end{wrapfigure}
-KFP provides multiple methods by which a machine learning developer can access on-demand synthetic data.
-Multiple methods of requesting and receiving faux data are provided.
-As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected synthesis method.
+KFP provides multiple methods by which a machine learning developer can access on-demand faux data.
+As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected generation method.
 Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
@@
 
-Limitations, areas for further research:
+Limitations, areas for further research - convert this to paragraph format:
 
@@
     \item Python module
-    \item Currently don't impose any kind of result set minimum size
+    \item Currently don't impose any kind of result set minimum size. Query pre-processor and synthesis process could optionally require a minimum source data size to improve privacy protection...
     \item Use in production
 \end{itemize}
+
+%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
+%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
+%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
+%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
 

### 2018-06-01 paper/seth.tex
Auto Update from local Sharelatex

@@
  \section{Reproducibility}
- %Good discussion of what reproducibilty vs replicability means
+ %Good discussion of what reproducibility vs replicability means
  %http://languagelog.ldc.upenn.edu/nll/?p=21956
@@
 Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
+
+ techniques for privacy protection:
+ * De-identifcation
+   * removal of known unique identifiers
+   * Data summarization to prevent individual identification
+ * Synthesis - Generating data based on some statistical model

### 2018-06-01 sourcecode/python/KungFauxPandas/DataSynthesizerPlugin.py
Tried to fix inheritance

@@ -14,13 +14,13 @@ except Exception as e:
     warnings.warn('DataSynthesizer source code appears to be absent.  This module will not function')
 
 
-from KungFauxPandas import PandaPlugin
-
+#from KungFauxPandas import PandaPlugin
+from KungFauxPandas.PandaPlugin import PandaPlugin as PandaPlug 
 
 ####################################################################################################################################
 ####################################################################################################################################
 
-class DataSynthesizerPlugin(PandaPlugin):
+class DataSynthesizerPlugin(PandaPlug):
     """ uses methods from <authors>'s Data Synthsizer to fauxify data """
 
     def __init__(self, df_in=None,

### 2018-06-01 sourcecode/python/KungFauxPandas/KDEPlugin.py

@@ -3,9 +3,10 @@
 ####################################################################################################################################
 
 #from KungFauxPandas import *
-from KungFauxPandas import PandaPlugin 
+#from KungFauxPandas import PandaPlugin 
+from KungFauxPandas.PandaPlugin import PandaPlugin as PandaPlug 
 
-class KDEPlugin(PandaPlugin):
+class KDEPlugin(PandaPlug):
     """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
     
     import pandas as pd

### 2018-06-01 sourcecode/python/KungFauxPandas/TrivialPlugin.py

@@ -2,15 +2,16 @@
 ####################################################################################################################################
 ####################################################################################################################################
 
-from KungFauxPandas import PandaPlugin 
+from KungFauxPandas.PandaPlugin import PandaPlugin as PandaPlug 
 
-class TrivialPlugin(PandaPlugin):
+class TrivialPlugin(PandaPlug):
     """ Returns the input as output. 
 	
 	Shows a basic example to build your own plugin"""
 
     def __init__(self):
-        PandaPlugin.__init__(self)
+        #PandaPlugin.__init__(self)
+        super(PandaPlugin,self).__init__()
 
 
     def fauxify(self, df_in=None):

### 2018-06-01 sourcecode/python/KungFauxPandas/kungfauxpandas.py

@@ -4,7 +4,7 @@ import numpy as np
 import scipy.stats as stats
 import sys
 import warnings
-import TrivialPlugin
+from KungFauxPandas import *
 
 ####################################################################################################################################
 ####################################################################################################################################

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

@@
 
-Some text about Table~\ref{included-methods} including why we built the KDE method, why DataSynthesizer, and why SGF% Not sure where this table should go....
+KFP provides a framework by which any number of methods for data privacy can be carried out.
+For demonstration purposes we have implemented three plugins that use different techniques for data synthesis, as shown in Table~\ref{included-methods}.
+The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware.
+The DataSynthesizer method, created by Ping et al.
+\cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
+Lastly, the Synthetic dataset Generation Framework by Bindschaedler et al.
+\cite{Bindschaedler2017} has ma
+
+Bindschaedler - shows synthetic data are close enough that models built with synthetic data are simlar to model built with real data.
+? Ping?
 

### 2018-06-01 paper/seth.tex
Auto Update from local Sharelatex

@@
    * Data summarization to prevent individual identification
- * Synthesis - Generating data based on some statistical model
+   * Problem: "Although these techniques support privacy protected data publishing without synthesis, the degree of privacy protection they provide depends on the background knowledge of adversaries."
+ * Synthesis - Generating data based on some statistical model; "...the process of creating artificial data that can be used to serve some key purposes of real data."

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

@@
 \subsection{System Structure}
-KFP provides a class
-
-Describe KFP's structure, including the ``plugin'' mechanism.
-
-Describe the SQL interface
 
@@
 
-% figure out how to adjust padding
-\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+\begin{wrapfigure}[15]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
   \centering
@@
 Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
+In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section.
 Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
@@
 \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
-Lastly, the Synthetic dataset Generation Framework by Bindschaedler et al.
-\cite{Bindschaedler2017} has ma
-
-Bindschaedler - shows synthetic data are close enough that models built with synthetic data are simlar to model built with real data.
-? Ping?
+Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al.
+\cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.
+For SGF and DataSynthesizer, their authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
+In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard.
+Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
 

### 2018-06-03 paper/autogit.sh
Auto Update from local Sharelatex

@@ -1,6 +1,7 @@
 #!/bin/bash
 cd /home/seth/kungfauxpandas/paper
 cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
+cp -rp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/images ./
 git pull
 git add *
 git commit -a -m 'Auto Update from local Sharelatex'  --author="magic-lantern <magic-lantern@users.noreply.github.com>"

### 2018-06-03 paper/main.tex
Auto Update from local Sharelatex

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2018}
+%\usepackage[final]{nips_2018}
 
@@
 
+% two references don't seem to represent a large body of published literature. Change wording? Include more references?
 There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
@@
 
+ Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
+Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
+One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by the traditional research paper \cite{schwab_making_2000}.
+The previously mentioned authors propose that reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
+Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
+
+% clarify this section; how does HIPAA allow data to be shared? BAA or De-identification are main methods
 In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.
@@
 
+% Logical step our work is taking. 
 One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.
@@
 
+% What is our major contribution to the area of reproducibility in machine learning?
 Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
 
+% this is a key unique feature of this work and should likely be repeated in conclusion. Perhaps also include in abstract
 This faux-data can be prodded, poked, plotted, and posted for the world to see, enabling analysts to develop their code using whatever means they prefer.
@@
 % some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
+% where to put this text?
+"Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
 
@@
 
+% Some information about minimum group size
 %* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)

### 2018-06-03 paper/autogit.sh
Changing order of operations so that web based edits are preserved if change occurs elsewhere.

@@ -1,8 +1,8 @@
 #!/bin/bash
 cd /home/seth/kungfauxpandas/paper
+git pull
 cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
 cp -rp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/images ./
-git pull
 git add *
 git commit -a -m 'Auto Update from local Sharelatex'  --author="magic-lantern <magic-lantern@users.noreply.github.com>"
 git push

### 2018-06-03 paper/main.tex
Auto Update from local Sharelatex

@@
   Kung Faux Pandas \\
-  \large Simplifying Privacy Protection
+  \large Simplifying privacy protection
   }
@@
 
+% this tool simplfies data sharing, simplifies data exploration within organizations
 \begin{abstract}
@@
 
+% somewhere - here? Explain that the environment has been provided with a randomly generated dataset similar to one researchers have worked with during anlysis of a Sepsis prediction model.
+
 \begin{figure}[ht]
@@
 
-Limitations, areas for further research - convert this to paragraph format:
+KFP provides a unique contirbution to the space of reproducible machine learning.
+Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data.
+However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a machine learning workflow.
 
-\begin{itemize}
-    \item Python module
-    \item Currently don't impose any kind of result set minimum size. Query pre-processor and synthesis process could optionally require a minimum source data size to improve privacy protection...
-    \item Use in production
-\end{itemize}
+While we have provided software code and a description of our methods in our GitHub repository, we believe that computational reproducibility should go beyond just making source code available.
+Peng recommends  making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
+This is a level of code sharing rarely achieved in machine learning research.
+Currently there is no standard long term format that works for all computational environments.
+For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI).
+We intend to continue this resesarch to make KFP available as a Python package.
 
-% Some information about minimum group size
-%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
-%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
-%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
-%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
+Another area that is open for further research is that of privacy protection through use of minimum dataset size.
+In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}.
+However, it is not clear that these methods are approiate for use machine learning in general or the specific domain of health care.
+Futhermore, effect size and probability to detect specific effects may vary by use case.
+Thus, in this work, no attempt has been made to constrain data set sizes or results returned.
+KFP could be modified to return no results if a minimum threshold is not met based on the risk profile of the data owner or, alternatively, data boosting techniques in combination with data synthesis could be used.
+
+The last area recommended for further research is to deploy and observe the use of KFP in an active machine learning environment where researchers are working with sensitive datasets.
+A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
+Additionally, as no private data was distributed via this system, actual review by security and compliance groups or IRBs may uncover additional requirements to reduce risk of data exposure that could require signicficant rework or futher study.
 
@@
 
-Basically need to put abstract here...
+It is proposed that this method will remove barriers to data access through ad-hoc non-protected genrated data sets.
+Additionally, we surmise that this tool will improve data exploration, allow researchers to develop data cleaning techniques without access to source data, and reduce dependency on complex processes required for data access.
+
+... other text from abstract or body of paper?...
 

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

@@
 The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
-Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate enabling reproducibility for some modern scientific endeavors such as machine learning.
-Perhaps the most important impediment to reproducibility is the need to share data.
+Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate for enabling reproducibility in some modern scientific endeavors such as machine learning.
+Perhaps the most important impediment to reproducibility is the need to share and have access to data.
 This has long been difficult in health care fields, but will presently become difficult for just about everyone.
 
-% two references don't seem to represent a large body of published literature. Change wording? Include more references?
-There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers from data, grouping individuals, and similar anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
 
-% explain faux here? faux data - similar to faux fur or faux leather - ethically more appealing, less expensive to produce or use
-% faux data is a broader term that encompasses any data privacy protection method - synthesis, anonymization, grouping, perturbation, etc.
-This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular use of data security methods into the popular Python Pandas data science library.
-For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.
+This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular combination of published privacy protection methods with the popular Python Pandas data science library\cite{mckinney-proc-scipy-2010}.
+KFP also provides a Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information though synthetic means or anonymization.
+We collectively refer to de-identified data and synthetic data as \emph{faux data}.
+Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
 
@@
 
+% shorten this? Is this the right place in the background for this?
  Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
@@
 
-% clarify this section; how does HIPAA allow data to be shared? BAA or De-identification are main methods
-In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.
-Thus, even institutions which share data face a steep institutional risk.
-This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.
+In the health care domain in the United States the key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
+HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}.
+There are two primary methods by which data can be shared or made public: de-identifcation, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement.
+Even institutions which share data within the confines of the laws face a steep institutional risk.
+These legal barriers makes it difficult to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.
 
-Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}, establishing a new paradigm in data ``ownership'' for that jurisdiction.
-In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
+Perhaps more ominously and broadly relevant for researchers, on May 25 , 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
+This law establishes a new paradigm in data ``ownership'' for that jurisdiction.
+This set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing that data to honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
 
+% continue re-writing from here
 These rules are ultimately good for citizens, but they create a pickle for scientists studying humans as it's very difficult to follow normal processes in scientific rigor while complying with privacy protection rules.
@@
 
+\section{System Details}
+
+% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
+% why not full synthesize a full dataset?
+limited to sql query where relevant data is brought together, easier to model 1 table than lots of separate tables.
+Modelling lots of separate tables requires extensive meta data configuration and a significant amount of computing power to generate...
+% where to put this text?
+"Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
+
 % What is our major contribution to the area of reproducibility in machine learning?
@@
 
-\section{System Details}
-
-% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
-% where to put this text?
-"Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
-
 Many methods of generating faux-data exist in the literature, many of which have software implementations freely available.
@@
 
-\subsection{System Structure}
+\subsection{System Architecture}
 
@@
 
-\subsection{Included Methods}
+\subsection{Included Synthesis Methods}
 

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

@@
 
-There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers from data, grouping individuals, and similar anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers, grouping individuals, and related anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
 
@@
 
+% previously had some information about various data anonymization and synthesis techniques. Put that back?
+
 \section{System Details}
@@
 % some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
-% why not full synthesize a full dataset?
-limited to sql query where relevant data is brought together, easier to model 1 table than lots of separate tables.
+% explain why not full synthesize a full dataset.
+better to limit to sql query where relevant data is brought together; easier to model 1 table than lots of separate tables.
 Modelling lots of separate tables requires extensive meta data configuration and a significant amount of computing power to generate...

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

@@
 HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}.
-There are two primary methods by which data can be shared or made public: de-identifcation, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement.
+There are two primary methods by which data can be shared or made public: de-identification, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement.
 Even institutions which share data within the confines of the laws face a steep institutional risk.
@@
 
-% continue re-writing from here
-These rules are ultimately good for citizens, but they create a pickle for scientists studying humans as it's very difficult to follow normal processes in scientific rigor while complying with privacy protection rules.
-
-% Logical step our work is taking. 
-One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.
-This is fairly straight-forward to implement.
-Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.
-The custodian then runs it and returns the results to the researcher.
-
-This has been technologically possible for some time, but it's awkward in practice because activities such as data cleaning, exploration, and plotting are interactive and iterative processes which would become impractical with a mediator.
-
-% previously had some information about various data anonymization and synthesis techniques. Put that back?
+The current legal environment creates a difficult situation for scientists in the health care domain.
+Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}.
+Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}.
+More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system, a tool to generate an entire outpatient Electronic Health Record (EHR) based on population statistics \cite{walonoski_synthea_2018}.
+Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.
 
@@
 "Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
+
+% Logical step our work is taking. 
+One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.
+This is fairly straight-forward to implement.
+Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.
+The custodian then runs it and returns the results to the researcher.
+
+This has been technologically possible for some time, but it's awkward in practice because activities such as data cleaning, exploration, and plotting are interactive and iterative processes which would become impractical with a mediator.
 
@@
 
-KFP provides a unique contirbution to the space of reproducible machine learning.
+KFP provides a unique contribution to the space of reproducible machine learning.
 Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data.
@@
 For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI).
-We intend to continue this resesarch to make KFP available as a Python package.
+We intend to continue this research to make KFP available as a Python package.
 
@@
 In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}.
-However, it is not clear that these methods are approiate for use machine learning in general or the specific domain of health care.
-Futhermore, effect size and probability to detect specific effects may vary by use case.
+However, it is not clear that these methods are appropriate for use machine learning in general or the specific domain of health care.
+Furthermore, effect size and probability to detect specific effects may vary by use case.
 Thus, in this work, no attempt has been made to constrain data set sizes or results returned.
@@
 A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
-Additionally, as no private data was distributed via this system, actual review by security and compliance groups or IRBs may uncover additional requirements to reduce risk of data exposure that could require signicficant rework or futher study.
+Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
 

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

@@
 KFP also provides a Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information though synthetic means or anonymization.
-We collectively refer to de-identified data and synthetic data as \emph{faux data}.
-Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
+We collectively refer to de-identified data and synthetic data as \emph{faux-data}.
+Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources.
 
@@
 
-% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
-% explain why not full synthesize a full dataset.
-better to limit to sql query where relevant data is brought together; easier to model 1 table than lots of separate tables.
-Modelling lots of separate tables requires extensive meta data configuration and a significant amount of computing power to generate...
 % where to put this text?
 "Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
+One way around the difficulties of source data access is to separate the dependency between data and analysis in such a way that analysis can be performed without the analyst having access to the source data.
+Such a process can be possible if a sufficiently detailed description of the sensitive data is provided.
+Appropriate models can be developed and initially validated before either being handed off to a data custodian who then runs the processes on protected data and returns the results to the researcher or access to the protected data has been granted directly to the researcher.
+Solutions of this form have been possible for some time, but are awkward in practice because activities such as data cleaning, exploration, and model building are interactive and iterative processes that require more than just descriptions of data.
 
-% Logical step our work is taking. 
-One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.
-This is fairly straight-forward to implement.
-Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.
-The custodian then runs it and returns the results to the researcher.
+KFP addresses the issue of data access by generating faux-data that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+This faux-data can be analyzed, cleaned, feature-engineered, etc.
+as if it were the actual source data.
+KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model.
+Three of these plug-ins are provided with full documentation for creating other plug-ins.
 
-This has been technologically possible for some time, but it's awkward in practice because activities such as data cleaning, exploration, and plotting are interactive and iterative processes which would become impractical with a mediator.
+As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability.
+To further the aim of reproducibility we have provided our code and a sample of a randomly generated data set for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
 
-% What is our major contribution to the area of reproducibility in machine learning?
-Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
-
-% this is a key unique feature of this work and should likely be repeated in conclusion. Perhaps also include in abstract
-This faux-data can be prodded, poked, plotted, and posted for the world to see, enabling analysts to develop their code using whatever means they prefer.
-When the analytical code is ready, it can then be sent to the data custodian to run on the real data.
-
-Many methods of generating faux-data exist in the literature, many of which have software implementations freely available.
-KFP provides a standard mechanism for ``wrapping'' any method into a ``plug-in'' which integrates the method with the Pandas data frame model.
-Three of these plug-ins are provided with full documentation for creating other plug-ins.
+KFP focuses on generating faux-data narrowed to a specific subset that a researcher is interested in rather than attempting to generate an entire population of data such as an entire EHR or longitudinal patient record.
+By focusing on just the data needed, performance is improved, the need for extensive modeling or metadata configuration is reduced, and the amount of faux-data generated and stored is minimized.
+Although the plugable methods included for faux-data generation have been shown to effectively replace source data for analysis, KFP facilitates a more through process that includes an initial exploration with faux-data followed by a repetition of methods on original source data through query logging and thereby aiding in replication.
 
@@
 The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
-However, as discussed previously, legal limitations and data protection processes are slow.
 Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
@@
 
-Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux data request/response process.
+Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process.
 All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
@@
 While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
-Previously removed "ORDER BY" clauses are re-applied to the faux data before results are returned to the user.
+Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
-
-% somewhere - here? Explain that the environment has been provided with a randomly generated dataset similar to one researchers have worked with during anlysis of a Sepsis prediction model.
 
@@
 \end{wrapfigure}
-KFP provides multiple methods by which a machine learning developer can access on-demand faux data.
-As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected generation method.
+KFP provides multiple methods by which a machine learning developer can access on-demand faux-data.
+As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method.
 Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
-Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
+Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
 In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section.
@@
 KFP provides a unique contribution to the space of reproducible machine learning.
-Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data.
+Through providing ad-hoc faux-data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
 However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a machine learning workflow.
 
-While we have provided software code and a description of our methods in our GitHub repository, we believe that computational reproducibility should go beyond just making source code available.
+While we have provided software code and a description of our methods, we believe that computational reproducibility should go beyond just making source code available.
 Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
@@
 
+Rather than the big step of full EHR synthesis or anonymization, KFP takes a small step in being a more usable small data generation tool. Big steps are harder to adopt...
+
 ... other text from abstract or body of paper?...

### 2018-06-04 paper/main.tex
some edits

--- 2018-06-04 paper/main.tex
@@
 \begin{abstract}
-A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.
-This system, which is publicly available \footnote{\url{https://github.com/CUD2V/kungfauxpandas}}, enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
+Kung Faux Pandas is an end-to-end system for easily generating synthetic data that is statistically similar to real data but lacks sensitive information.
+This publicly available \footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system lowers barriers to HIPAA- and GDPR-compliant data sharing for reproducibility testing and other purposes.
 \end{abstract}
@@
 
-The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
-Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate for enabling reproducibility in some modern scientific endeavors such as machine learning.
-Perhaps the most important impediment to reproducibility is the need to share and have access to data.
-This has long been difficult in health care fields, but will presently become difficult for just about everyone.
+Independent reproduction and replication of results are critical components of scientific inquiry.
+Barriers to data access and sharing are the most important impediments to reproducibility in computational research.
+Health care research has unique challenges because of necessary personal data privacy protections.
 
-There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers, grouping individuals, and related anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariable relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}).
+However, no pipeline currently exists with which computational investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing.
+This work addresses that gap.
 
-This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular combination of published privacy protection methods with the popular Python Pandas data science library\cite{mckinney-proc-scipy-2010}.
-KFP also provides a Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information though synthetic means or anonymization.
-We collectively refer to de-identified data and synthetic data as \emph{faux data}.
-Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
+We have created an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular combination of established privacy protection methods with the popular Python Pandas data science library\cite{mckinney-proc-scipy-2010}.
+KFP also provides a Structured Query Language (SQL) interface which enables users to query a database and receive a data set without personal information through either anonymization or synthetic data generation.
 
@@
 % shorten this? Is this the right place in the background for this?
- Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
-Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
-Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by the traditional research paper \cite{schwab_making_2000}.
-The previously mentioned authors propose that reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
-Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+Recent work has clarified the definition and importance of reproducibility and a closely related entity, replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion.\cite{drummond_replicability_2009} Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
+One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
+These items are difficult to completely convey in a traditional research paper \cite{schwab_making_2000}.
+In the context of machine learning (ML), sufficient detail is required such that an independent investigator could create the same hardware and software configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
 Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
@@
 % What is our major contribution to the area of reproducibility in machine learning?
-Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+KFP sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+We collectively refer to de-identified data and synthetic data as \emph{faux data}.
+Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
 

### 2018-06-04 paper/main.tex
more edits

@@
 
-Perhaps more ominously and broadly relevant for researchers, on May 25 , 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
+Perhaps more ominously and broadly relevant for researchers, on May 25, 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
 This law establishes a new paradigm in data ``ownership'' for that jurisdiction.
@@
 % What is our major contribution to the area of reproducibility in machine learning?
-KFP sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+KFP sidesteps this problem by generating \emph{faux data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
 We collectively refer to de-identified data and synthetic data as \emph{faux data}.
-Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
+We use the word faux in its standard sense of artificial or fake, but more specifically as it is used in fashion: man-made materials that look and feel like real leather, fur, etc., but wihout the problematic derivation from live animals and reliance upon limited resources.
 
@@
 
-Many methods of generating faux-data exist in the literature, many of which have software implementations freely available.
+Many methods of generating faux data exist, some with freely available software implementations.
 KFP provides a standard mechanism for ``wrapping'' any method into a ``plug-in'' which integrates the method with the Pandas data frame model.
@@
 
-The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
-However, as discussed previously, legal limitations and data protection processes are slow.
-Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
+Ideally, a computational investigator can develop, test, and validate models using all available data.
+However, as discussed previously, regulatory limitations may prevent data access.
+Even with regulatory approvals, data access processes can be slow.
+Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand.
 
@@
 
-Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux data request/response process.
+Figure~\ref{fig:synthesis_process} shows the automated faux data request/response process.
 All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
@@
 Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
-While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
+While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods.
 Previously removed "ORDER BY" clauses are re-applied to the faux data before results are returned to the user.
@@
 \end{wrapfigure}
-KFP provides multiple methods by which a machine learning developer can access on-demand faux data.
+KFP provides multiple methods by which a ML developer can access on-demand faux data.
 As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected generation method.
-Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
+Data can either be viewed directly in browser or downloaded in csv format for use in a ML process.
 Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query.
@@
     \toprule
-    Method                                 & Source                    & Notes \\
+    Method                                                 & Notes \\
     \midrule
-    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
-    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
-    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
+    Kernel Density Estimator\cite{silverman_density_1986}              & Inter-related ordinal and ratio data\\
+    DataSynthesizer\cite{ping17datasynthesizer}                                 & Bayesian modeling of column relationships\\
+    Synthetic Generation Framework\cite{Bindschaedler2017}      & Probabilistic modeling\\
     \bottomrule
@@
 
-KFP provides a unique contirbution to the space of reproducible machine learning.
+KFP provides a unique contribution to the space of reproducible ML.
 Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data.

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

--- 2018-06-04 paper/main.tex
@@
 \begin{abstract}
-A description of an end-to-end system for easily generating faux-data which is statistically similar to given real data but does not contain sensitive personal information.
-This system, which is publicly available \footnote{\url{https://github.com/CUD2V/kungfauxpandas}}, enables data to be distributed for reproducibility testing and other purposes while in full compliance with HIPAA and GDPR.
+There are many barriers to data access in data sharing, especially in the domain of machine learning on health care data.
+Legal constraints such as HIPAA protect patient privacy but slow access to data and limit reproducibility.
+We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to given real data but does not contain sensitive health information.
+This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project.
+Kung Faux Pandas is open source and publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}}.
 \end{abstract}
@@
 
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=120mm]{data_synthesis_process}
+  \caption{Data synthesis process.}
+  \label{fig:synthesis_process}
+\end{figure}
+
 Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process.
@@
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=120mm]{data_synthesis_process}
-  \caption{Data synthesis process.}
-  \label{fig:synthesis_process}
-\end{figure}
 
@@
 
-It is proposed that this method will remove barriers to data access through ad-hoc non-protected genrated data sets.
-Additionally, we surmise that this tool will improve data exploration, allow researchers to develop data cleaning techniques without access to source data, and reduce dependency on complex processes required for data access.
+KFP removes barriers to data access and data sharing via self-service faux-data generation.
+Users of KFP do not need to have access to a protected dataset nor does a human have to be involved in translating researchers data needs into a non-protected dataset.
+This self-service data can be differentially private or meet other privacy needs based on plugin capabilities.
+With faux-data, researchers can publicly share data upon which their research relies without organizational fear of privacy breaches.
+KFP also facilitates a process by which evaluation, analysis, or model building is first performed with faux-data followed by repetition upon private data.
 
-Rather than the big step of full EHR synthesis or anonymization, KFP takes a small step in being a more usable small data generation tool. Big steps are harder to adopt...
-
-... other text from abstract or body of paper?...
+Finally, instead of taking the computational and labor intensive step of full EHR de-identification or synthesis, KFP takes the smaller and more easily implemented step of just-in-time data de-identification or synthesis.
+We surmise that this tool will improve data exploration and reduce dependency on complex processes required for data access.
+The result of this system will be improved reproducibility in machine learning.
 

### 2018-06-04 sourcecode/python/create_logging_db.py
Saving query logging code and a few other changes

@@ -1,0 +1,23 @@
+import sqlite3
+
+db_file = '../../data/kfp_log.db'
+
+sql_create_kfp_table = """
+    CREATE TABLE IF NOT EXISTS kfp_log (
+        query TEXT NOT NULL,
+        query_start TEXT NOT NULL,
+        query_end TEXT NOT NULL,
+        query_result BLOB,
+        faux_method TEXT NOT NULL,
+        fauxify_start TEXT NOT NULL,
+        fauxify_end TEXT NOT NULL,
+        faux_result BLOB
+    ); """
+
+try:
+    conn = sqlite3.connect(db_file)
+    c = conn.cursor()
+    c.execute(sql_create_kfp_table)
+    conn.commit()
+except Exception as e:
+    print('Exception encountered when creating table:', e)

### 2018-06-04 sourcecode/python/kungfauxpandas.py

@@ -4,6 +4,8 @@ import numpy as np
 import scipy.stats as stats
 import sys
 import warnings
+import datetime
+import sqlite3
 
 library_location = '../../plugins/DataSynthesizer'
 sys.path.append(library_location)
@@ -247,33 +249,70 @@ class KDEPlugin(PandaPlugin):
 class KungFauxPandas(object):
 
     # To do:  Check to see if a column is unique (i.e. index) and recreate with unique < maybe use sample without replacement?>
-
-    def __init__(self, plugin=TrivialPlugin(), verbose=True):
+    # if enabling logging, make sure database and required log table has been
+    #   properly created - see create_logging_db.py
+    def __init__(self, plugin=TrivialPlugin(), verbose=True, logging=True, db_file=None):
 
         self.verbose = verbose
         self.seed = 10293510
         self.plugin = plugin
         self.synthesis_methods = ('Trivial', 'KDE', 'DataSynthesizer')
+        if db_file is None:
+            self.db_file = '../../data/kfp_log.db'
+        self.logging = logging
+
+        if self.logging:
+            self.logging_conn = sqlite3.connect(self.db_file)
+            self.logging_cur = self.logging_conn.cursor()
 
     #- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
     def read_sql(self, sql, conn, **kwargs):
 
         self.sql = sql
         self.conn = conn
+
+        if(self.logging):
+            query_start = datetime.datetime.now()
         self.df_in = pd.read_sql(self.sql, self.conn, **kwargs)
-        self.df_out = self.plugin.fauxify(self.df_in)
+        if(self.logging):
+            query_end = datetime.datetime.now()
+        try:
+            self.df_out = self.plugin.fauxify(self.df_in)
+        except Exception as e:
+            print('kungfauxpandas.read_sql() exception while attempting to fauxify data:', e)
+            raise
+        if(self.logging):
+            fauxify_end = datetime.datetime.now()
+
+            try:
+                sql = '''
+                    INSERT INTO kfp_log(
+                        query,
+                        query_start,
+                        query_end,
+                        query_result,
+                        faux_method,
+                        fauxify_start,
+                        fauxify_end,
+                        faux_result
+                        )
+                    VALUES(?,?,?,?,?,?,?,?)
+                    '''
+                self.logging_cur.execute(sql, (
+                    self.sql,
[…]

### 2018-06-04 sourcecode/python/tests/test_kungfauxpandas.py

@@ -1,0 +1,1 @@
+# put unit test code here

### 2018-06-04 sourcecode/python/web-service.py

@@ -110,7 +110,7 @@ def synthesize_data(query: hug.types.text, method: hug.types.text):
               'response': df_html,
               'csv': df.to_csv(index=False)}
         except Exception as e:
-            print('Caught exception', str(e))
+            print('web-service.synthesize_data() caught exception', str(e))
             return {
                 'message': 'error',
                 'query': '{0}'.format(query),

### 2018-06-05 sourcecode/python/kungfauxpandas.py
Changing back to correlated attribute mode

@@ -51,7 +51,7 @@ class DataSynthesizerPlugin(PandaPlugin):
     """ Constructs column-wise (i.e. ignore covariances) fake data based on input df. """
 
     def __init__(self, df_in=None,
-            mode = 'independent_attribute_mode',
+            mode = 'correlated_attribute_mode',
             threshold_value = 20,
             categorical_attributes = {},
             candidate_keys = {},

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

@@
 \begin{abstract}
-There are many barriers to data access in data sharing, especially in the domain of machine learning on health care data.
+There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data.
 Legal constraints such as HIPAA protect patient privacy but slow access to data and limit reproducibility.
-We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to given real data but does not contain sensitive health information.
+We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to given real data but lacks sensitive information.
 This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project.
-Kung Faux Pandas is open source and publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}}.
+Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.
 \end{abstract}

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

@@
 KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model.
-Three of these plug-ins are provided with full documentation for creating other plug-ins.
+Two of these plug-ins are provided with full documentation for creating other plug-ins.
 
@@
 
+Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process.
+All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
 \begin{figure}[ht]
@@
 \end{figure}
-
-Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process.
-All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
 All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries.
@@
 KFP provides a framework by which any number of methods for data privacy can be carried out.
-For demonstration purposes we have implemented three plugins that use different techniques for data synthesis, as shown in Table~\ref{included-methods}.
+For demonstration purposes we have implemented two plugins that use different techniques for data synthesis.
 The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware.
@@
 \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
-Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al.
-\cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.
-For SGF and DataSynthesizer, their authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
-In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard.
-Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
-
-\begin{table}
-  \caption{Kung Faux Pandas data synthesis methods}
-  \label{included-methods}
-  \centering
-  \begin{tabular}{p{12em} l p{14em}}
-    \toprule
-    Method                                 & Source                    & Notes \\
-    \midrule
-    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
-    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
-    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
-    \bottomrule
-  \end{tabular}
-\end{table}
+In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
 
@@
 
+% include some of this? 
+% Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al.
+\cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.
+In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard.
+Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
+
 \section{Conclusion}

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

@@
 \graphicspath{ {./images/} }
-\usepackage{soul}           % added by seth - remove before submission, provides highlighting support
 \usepackage{wrapfig}        % added by seth for placing images in-line with text
@@
 
-The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.
-Unfortunately, the mechanisms of communicating scientific results have changed little since the age of enlightenment and are inadequate for enabling reproducibility in some modern scientific endeavors such as machine learning.
-Perhaps the most important impediment to reproducibility is the need to share and have access to data.
-This has long been difficult in health care fields, but will presently become difficult for just about everyone.
+Independent reproduction and replication of results are critical components of scientific inquiry.
+Barriers to data access and sharing are the most important impediments to reproducibility in machine learning (ML) research.
+Health care research has unique challenges because of necessary personal data privacy protections.
 
-There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers, grouping individuals, and related anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.
+Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariable relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}).
+However, no pipeline currently exists with which ML investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing.
+This work addresses that gap.
 
-This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular combination of published privacy protection methods with the popular Python Pandas data science library\cite{mckinney-proc-scipy-2010}.
-KFP also provides a Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information though synthetic means or anonymization.
-We collectively refer to de-identified data and synthetic data as \emph{faux-data}.
-Faux in it's standard sense of artificial or fake, but more specifically as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources.
+We have created an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular combination of established privacy protection methods with the popular Python Pandas data science library\cite{mckinney-proc-scipy-2010}.
+KFP also provides a Structured Query Language (SQL) interface which enables users to query a database and receive a data set without personal information through either anonymization or synthetic data generation.
 
@@
 
-% shorten this? Is this the right place in the background for this?
- Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability.
-Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}.
-Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by the traditional research paper \cite{schwab_making_2000}.
-The previously mentioned authors propose that reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}.
-Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+Recent work has clarified the definition and importance of reproducibility and a closely related concept, replicability.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion.\cite{drummond_replicability_2009} Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
+One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
+These items are difficult to completely convey in a traditional research paper \cite{schwab_making_2000}.
+
+In the context of ML, sufficient detail is required such that an independent investigator could create the same hardware and software configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
 Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
@@
 Even institutions which share data within the confines of the laws face a steep institutional risk.
-These legal barriers makes it difficult to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.
+These legal barriers makes it difficult to enable independent verification of ML models which often require enormous amounts of training data.
 
-Perhaps more ominously and broadly relevant for researchers, on May 25 , 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
+Perhaps more ominously and broadly relevant for researchers, on May 25, 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
 This law establishes a new paradigm in data ``ownership'' for that jurisdiction.
@@
 
-KFP addresses the issue of data access by generating faux-data that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+KFP addresses the issue of data access by generating data that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+We collectively refer to de-identified data and synthetic data as \emph{faux-data}.
+We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources.
 This faux-data can be analyzed, cleaned, feature-engineered, etc.
@@
 
-The ideal environment for a machine learning developer to develop, test, or validate a model is to have unfettered access to all data in the problem domain they are working in.
-Figure~\ref{fig:architecture} depicts a basic architecture of an alternative to direct data access: data access through an intermediary that can synthesize data on-demand.
+Ideally a ML investigator should develop, test, and validate models using all available data.
+This is most easily accomplished when they have unfettered access to all data in the problem domain they are working in.
+Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand.
 
@@
 
-Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process.
+Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process.
 All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
@@
 Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
-While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods.
+While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods.
 Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
@@
 \end{wrapfigure}
-KFP provides multiple methods by which a machine learning developer can access on-demand faux-data.
+KFP provides multiple methods by which a ML developer can access on-demand faux-data.
 As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method.
-Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process.
-Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
+Data can either be viewed directly in browser or downloaded in csv format for use in a ML process.
+Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
 In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section.
@@
 
-KFP provides a unique contribution to the space of reproducible machine learning.
-Through providing ad-hoc faux-data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
-However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a machine learning workflow.
+KFP provides a unique contribution to the space of reproducible ML.
+Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
+However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a ML workflow.
 
-While we have provided software code and a description of our methods, we believe that computational reproducibility should go beyond just making source code available.
+While we have provided software code and a description of our methods, we believe that ML reproducibility should go beyond just making source code available.
 Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
-This is a level of code sharing rarely achieved in machine learning research.
+This is a level of code sharing rarely achieved in ML research.
 Currently there is no standard long term format that works for all computational environments.
@@
 In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}.
-However, it is not clear that these methods are appropriate for use machine learning in general or the specific domain of health care.
+However, it is not clear that these methods are appropriate for use ML in general or the specific domain of health care.
 Furthermore, effect size and probability to detect specific effects may vary by use case.
@@
 
-The last area recommended for further research is to deploy and observe the use of KFP in an active machine learning environment where researchers are working with sensitive datasets.
+The last area recommended for further research is to deploy and observe the use of KFP in an active ML environment where researchers are working with sensitive datasets.
 A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
@@
 We surmise that this tool will improve data exploration and reduce dependency on complex processes required for data access.
-The result of this system will be improved reproducibility in machine learning.
+The result of this system will be improved reproducibility in ML.
 

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

@@
 
-In the health care domain in the United States the key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
+Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data.
+As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
 HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}.
-There are two primary methods by which data can be shared or made public: de-identification, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement.
-Even institutions which share data within the confines of the laws face a steep institutional risk.
-These legal barriers makes it difficult to enable independent verification of ML models which often require enormous amounts of training data.
-
-Perhaps more ominously and broadly relevant for researchers, on May 25, 2018 the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}.
-This law establishes a new paradigm in data ``ownership'' for that jurisdiction.
-This set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing that data to honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.
+While there are other domain specific data privacy laws, there are also some broad rules that affect entire countries such as the European Union's General Data Protection Regulation (GDPR).
+The GDPR puts in place new rules about data ownership and control in an attempt to give individuals more control over their information.
 
@@
 
-Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process.
-All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
 \begin{figure}[ht]
@@
 \end{figure}
+
+Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process.
+All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
 All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries.

### 2018-06-05 paper/long_version.tex
Auto Update from local Sharelatex

--- 2018-06-05 paper/main.tex
@@
 \graphicspath{ {./images/} }
-\usepackage{wrapfig}        % added by seth for placing images in-line with text
 
@@
   James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
-  Data Science to Patient Value (D2V)\\
-  School of Medicine\\
-  University of Colorado Anschutz Medical Campus\\
-  Aurora, CO\\
+  Data Science to Patient Value (D2V), School of Medicine\\
+  University of Colorado Anschutz Medical Campus, Aurora, CO\\
   \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
@@
 
-% this tool simplfies data sharing, simplifies data exploration within organizations
 \begin{abstract}
@@
 Legal constraints such as HIPAA protect patient privacy but slow access to data and limit reproducibility.
-We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to given real data but lacks sensitive information.
+We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information.
 This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project.
@@
 Recent work has clarified the definition and importance of reproducibility and a closely related concept, replicability.
-Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion.\cite{drummond_replicability_2009} Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion\cite{drummond_replicability_2009}.
+Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
 One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
@@
 As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
-HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}.
+HIPAA is backed by significant civil penalties as well as specifics about data security and what can and cannot be done with protected health information \cite{hippaviol}.
 While there are other domain specific data privacy laws, there are also some broad rules that affect entire countries such as the European Union's General Data Protection Regulation (GDPR).
@@
 As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability.
-To further the aim of reproducibility we have provided our code and a sample of a randomly generated data set for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
+To further the aim of reproducibility we have provided our code and a sample of a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
 
@@
 \end{figure}
-
 \begin{figure}[ht]
@@
 
-\begin{wrapfigure}[15]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
-  \centering
-  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
-  \caption{User Interface.}
-  \label{fig:ui}
-\end{wrapfigure}
 KFP provides multiple methods by which a ML developer can access on-demand faux-data.
@@
 Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{ui_screenshot3}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{figure}
 
@@
 Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
-However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a ML workflow.
+However, there are several areas that could be improved or researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
 
@@
 
-Another area that is open for further research is that of privacy protection through use of minimum dataset size.
-In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}.
-However, it is not clear that these methods are appropriate for use ML in general or the specific domain of health care.
-Furthermore, effect size and probability to detect specific effects may vary by use case.
-Thus, in this work, no attempt has been made to constrain data set sizes or results returned.
-KFP could be modified to return no results if a minimum threshold is not met based on the risk profile of the data owner or, alternatively, data boosting techniques in combination with data synthesis could be used.
+Another area that is open for further research is that of domain and institution specific data privacy needs.
+In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009} as the key method for privacy protection.
+However, it is not clear that these methods are appropriate for use in ML in general or domains other than education.
+Thus, in this work, no attempt has been made to constrain data set sizes nor provide additional proofs of data protection.
+KFP could be modified to return no results if a minimum threshold is not met or, alternatively, data boosting techniques in combination with data synthesis could be used based on the risk profile of the data owner(s).
 
@@
 Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
-
 % include some of this? 

### 2018-06-05 paper/seth.tex
Auto Update from local Sharelatex

@@
  * Synthesis - Generating data based on some statistical model; "...the process of creating artificial data that can be used to serve some key purposes of real data."
+
+ % Some information about minimum group size
+ %* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
+ %* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
+ %* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
+ %* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
+
+ % removed since we never got SGF working
+ \begin{table}
+  \caption{Kung Faux Pandas data synthesis methods}
+  \label{included-methods}
+  \centering
+  \begin{tabular}{p{12em} l p{14em}}
+    \toprule
+    Method                                 & Source                    & Notes \\
+    \midrule
+    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
+    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
+    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{wrapfigure}[15]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+  \centering
+  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{wrapfigure}

### 2018-06-05 paper/short_version.tex
Auto Update from local Sharelatex

--- 2018-06-05 paper/long_version.tex
@@
 \graphicspath{ {./images/} }
+\usepackage{wrapfig}        % added by seth for placing images in-line with text
 
@@
 
-% where to put this text?
-"Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
 One way around the difficulties of source data access is to separate the dependency between data and analysis in such a way that analysis can be performed without the analyst having access to the source data.
@@
 This is most easily accomplished when they have unfettered access to all data in the problem domain they are working in.
-Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand.
+The novel architecture of KFP is that direct data access is provided through an intermediary that can synthesize data on-demand.
 
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{prototype_architecture}
-  \caption{System Architecture.}
-  \label{fig:architecture}
-\end{figure}
 \begin{figure}[ht]
@@
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
-
+\begin{wrapfigure}[16]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+  \centering
+  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
+  \caption{User Interface.}
+  \label{fig:ui}
+\end{wrapfigure}
 KFP provides multiple methods by which a ML developer can access on-demand faux-data.
@@
 Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{ui_screenshot3}
-  \caption{User Interface.}
-  \label{fig:ui}
-\end{figure}
 
@@
 Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
-% include some of this? 
-% Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al.
-\cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.
-In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard.
-Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
 

### 2018-06-05 paper/short_version.tex
Auto Update from local Sharelatex

@@
   University of Colorado Anschutz Medical Campus, Aurora, CO\\
-  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
-  }
+  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}}
 
@@
 Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}.
-More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system, a tool to generate an entire outpatient Electronic Health Record (EHR) based on population statistics \cite{walonoski_synthea_2018}.
+More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system \cite{walonoski_synthea_2018}.
 Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.
@@
 
-KFP focuses on generating faux-data narrowed to a specific subset that a researcher is interested in rather than attempting to generate an entire population of data such as an entire EHR or longitudinal patient record.
+KFP focuses on generating faux-data narrowed to a specific subset that a researcher is interested in rather than attempting to generate an entire population of data such as an entire EHR.
 By focusing on just the data needed, performance is improved, the need for extensive modeling or metadata configuration is reduced, and the amount of faux-data generated and stored is minimized.
@@
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
+
 \begin{wrapfigure}[16]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
@@
 \end{wrapfigure}
+
 KFP provides multiple methods by which a ML developer can access on-demand faux-data.

### 2018-06-05 paper/short_version.tex
Auto Update from local Sharelatex

@@
 Recent work has clarified the definition and importance of reproducibility and a closely related concept, replicability.
-Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} Others have used the terms in a reverse fashion\cite{drummond_replicability_2009}.
-Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
+Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result."\cite{leek_opinion_2015,peng_reproducible_2006} There is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
 One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
-These items are difficult to completely convey in a traditional research paper \cite{schwab_making_2000}.
+These items are difficult to convey in a traditional research paper \cite{schwab_making_2000}.
 
@@
 
-Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data.
-As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
-HIPAA is backed by significant civil penalties as well as specifics about data security and what can and cannot be done with protected health information \cite{hippaviol}.
-While there are other domain specific data privacy laws, there are also some broad rules that affect entire countries such as the European Union's General Data Protection Regulation (GDPR).
+Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models due to data access issues.
+As an example, in the health care domain in the US, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
+HIPAA is backed by significant civil penalties, specifics about data security, and what can be done with protected health information \cite{hippaviol}.
+While there are other domain specific data privacy laws, there are also some broad rules such as the European Union's General Data Protection Regulation (GDPR).
 The GDPR puts in place new rules about data ownership and control in an attempt to give individuals more control over their information.
 
-The current legal environment creates a difficult situation for scientists in the health care domain.
 Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}.
-Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}.
 More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system \cite{walonoski_synthea_2018}.
-Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.
+Current solutions are not without their drawbacks however as many require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.
 
@@
 
-KFP addresses the issue of data access by generating data that is ``statistically similar'' to the real data but does not itself contain any sensitive data.
+KFP addresses the issue of data access by generating data that is similar to the real data but does not itself contain any sensitive data.
 We collectively refer to de-identified data and synthetic data as \emph{faux-data}.
 We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources.
-This faux-data can be analyzed, cleaned, feature-engineered, etc.
+Faux-data can be analyzed, cleaned, modeled etc.
 as if it were the actual source data.
@@
   \centering
-  \includegraphics[width=120mm]{data_synthesis_process}
+  \includegraphics[width=120mm]{prototype_architecture}
+  \caption{System Architecture.}
+  \label{fig:architecture}
+\end{figure}\begin{figure}[ht]
+  \centering
+  \includegraphics[width=100mm]{data_synthesis_process}
   \caption{Data synthesis process.}
@@
 Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
-While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods.
-Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
-Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
-
-\begin{wrapfigure}[16]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
+While the current
+\begin{wrapfigure}[15]{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
   \centering
@@
 \end{wrapfigure}
+implementation only utilizes a couple of synthesis methods, ML developers or data owners can insert their own custom method or modify existing methods.
+Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
+Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
 
@@
 Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
-However, there are several areas that could be improved or researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
+However, there are several areas that could be researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
 
 While we have provided software code and a description of our methods, we believe that ML reproducibility should go beyond just making source code available.
-Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
+Peng recommends that code should be made available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
 This is a level of code sharing rarely achieved in ML research.
@@
 However, it is not clear that these methods are appropriate for use in ML in general or domains other than education.
-Thus, in this work, no attempt has been made to constrain data set sizes nor provide additional proofs of data protection.
 KFP could be modified to return no results if a minimum threshold is not met or, alternatively, data boosting techniques in combination with data synthesis could be used based on the risk profile of the data owner(s).
@@
 A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
-Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
+Additionally, actual reviews by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
 

### 2018-06-07 paper/autogit.sh
Fixing autogit so it only commits changes in the paper directory.

@@ -4,5 +4,5 @@ git pull
 cp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/*.{tex,bib,sty} ./
 cp -rp /home/seth/sharelatex/sharelatex_data/data/compiles/5aecc5ba3a518f007ab52133-5aeb8780c8a91e016452182f/images ./
 git add *
-git commit -a -m 'Auto Update from local Sharelatex'  --author="magic-lantern <magic-lantern@users.noreply.github.com>"
+git commit -m 'Auto Update from local Sharelatex'  --author="magic-lantern <magic-lantern@users.noreply.github.com>"
 git push

### 2018-06-10 paper/long_version.tex
Auto Update from local Sharelatex

@@
 
+\section{Experiments}
+Tested this on a Ubuntu 16.04 Linux virtual machine running on Virtual Box with 12 CPUs and 64GB of RAM allocated from the host system.
+
+Running the query shown in the UI screenshot
+
+rows: query time: method: fauxify time:
+1k
+10k
+100k
+1000k
+
+Data from notebook performance\_tests.ipynb
+
+\begin{table}
+  \caption{Kung Faux Pandas data synthesis method timings}
+  \label{included-methods}
+  \centering
+  \begin{tabular}{p{12em} l p{14em}}
+    \toprule
+    Method                                 & Source                    & Notes \\
+    \midrule
+    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
+    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
+    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Brief explaination of each method.
+
+hmm, that's interesting
+
 \section{Discussion}

### 2018-06-10 paper/long_version.tex
Auto Update from local Sharelatex

@@
 
-Brief explaination of each method.
+\begin{table}
+  \caption{Kung Faux Pandas data synthesis plugin timings (seconds)}
+  \label{timing_results}
+  \centering
+    \begin{tabular}{l c c c c c}
+    	\toprule 
+    	Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
+    	\midrule 
+    	Trivial & x.y (1.04) & x.y (1.04) &  &  &  \\ 
+    	KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 
+    	DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
+    	DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
+    	DS Independent & x.y (1.04) &  &  &  &  \\ 
+    	DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
+    	\midrule
+    \end{tabular}
+\end{table}
 
-hmm, that's interesting
+Brief explanation of each method.
+
+hmm, that's interesting. Describe what this means...
 

### 2018-06-10 paper/long_version.tex
Auto Update from local Sharelatex

--- 2018-06-05 paper/long_version.tex
@@
 \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
+As a result of their methods, the DataSynthezier offers a unique contribution to the space: it can work with no configuration other than input data, or can be configured to provide more custom results.
 In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
+
+\section{Experiments}
+
+In this section we evaluate the performance of the KFP plugins to see how closely the methods meet the stated goals of ease of use, similarity to input data, and total time to run.
+Hardware for these performance and evaluation tests were on a 2017 MacBook Pro, 3.1 GHz Intel Core i7, 16GB 2133 MHz LPDDR3 with macOS 10.12.6.
+KFP software is written in Python 3.6; all packages and dependencies can be installed with identifical versions using the provided requirements.txt, environment.yml file, or Docker container.
+Database queries were run against the relational database PostgreSQL version 9.6.9.
+Data was generated using the notebook test\_data\_generator.ipynb available in our GitHub repository.
+The sample data are composed of 100,000 patient encounters with various dimensions spread across several tables, the largest of which contains 10,539,550 rows of data.
+
+\subsection{Timing}
+
+Table~\ref{timing_results} documents results obtained from running the various plugins.
+Source code for running performance tests are available in the Jupyter notebook performance\_tests.ipynb.
+The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct performance of the plugin class and function overloading mechanism as returns the input data frame unmodified.
+The KDE method is the custom developed method that acts as an example of how to create plugins.
+A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences.
+Independent mode generates synthetic data with each attribute being modeled independently from the others.
+Correlated attribute mode finds inter-column relationships to more accurately generate synthetic data.
+Both DataSynthesizer modes are run with no configuration and "w/Config" by passing in some column-wise dataset specific configuration.
+
+\begin{table}
+	\caption{Kung Faux Pandas data synthesis plugin timings (seconds)}
+	\label{timing_results}
+	\centering
+	\begin{tabular}{l c c c c c}
+		\toprule 
+		Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
+		\midrule 
+		Trivial & x.y (1.04) & x.y (1.04) &  &  &  \\ 
+		KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 
+		DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
+		DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
+		DS Independent & x.y (1.04) &  &  &  &  \\ 
+		DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
+		\midrule
+	\end{tabular}
+\end{table}
+
+hmm, that's interesting. Describe what this means...
 

### 2018-06-11 paper/long_version.tex
Auto Update from local Sharelatex

@@
 Data was generated using the notebook test\_data\_generator.ipynb available in our GitHub repository.
-The sample data are composed of 100,000 patient encounters with various dimensions spread across several tables, the largest of which contains 10,539,550 rows of data.
+The sample data are composed of 100,000 patient encounters with various dimensions spread across several tables, the largest of which contains 10,539,549 rows of data.
 
@@
 		\midrule 
-		Trivial & x.y (1.04) & x.y (1.04) &  &  &  \\ 
+		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e06 \\ 
 		KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 

### 2018-06-11 paper/long_version.tex
Auto Update from local Sharelatex

@@
 \begin{table}
-	\caption{Kung Faux Pandas data synthesis plugin timings (seconds)}
+	\caption{Kung Faux Pandas data synthesis plugin timings (mean seconds)}
 	\label{timing_results}
@@
 		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e06 \\ 
-		KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 
+		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
 		DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 

### 2018-06-11 paper/long_version.tex
Auto Update from local Sharelatex

@@
 There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data.
-Legal constraints such as HIPAA protect patient privacy but slow access to data and limit reproducibility.
+Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility.
 We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information.
@@
 In this section we evaluate the performance of the KFP plugins to see how closely the methods meet the stated goals of ease of use, similarity to input data, and total time to run.
-Hardware for these performance and evaluation tests were on a 2017 MacBook Pro, 3.1 GHz Intel Core i7, 16GB 2133 MHz LPDDR3 with macOS 10.12.6.
+Hardware for these performance and evaluation tests were from a 2017 MacBook Pro, 3.1 GHz Intel Core i7, 16GB 2133 MHz LPDDR3 with macOS 10.12.6.
 KFP software is written in Python 3.6; all packages and dependencies can be installed with identifical versions using the provided requirements.txt, environment.yml file, or Docker container.
@@
 Data was generated using the notebook test\_data\_generator.ipynb available in our GitHub repository.
-The sample data are composed of 100,000 patient encounters with various dimensions spread across several tables, the largest of which contains 10,539,549 rows of data.
+The sample data population is composed of 100,000 patient encounters with various dimensions spread across several tables, the largest of which contains 10,539,549 rows of data.
+The sample query generating the "real" input data is composed of 8 total columns composed of IDs, categorical variables, and floating point numbers.
 
@@
 		\midrule 
-		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e06 \\ 
+		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e-06 \\ 
 		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
-		DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
-		DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
-		DS Independent & x.y (1.04) &  &  &  &  \\ 
-		DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
+		DS Correlated & 0.188 & 1.419 & 3.460 & 16.66 & 159.9 \\ 
+		DS Correlated w/Config & 0.172 & 0.627 & 1.393 & 342.7 &  \\ 
+		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\ 
+		DS Independent w/Config &  &  &  &  &  \\
 		\midrule
@@
 
-hmm, that's interesting. Describe what this means...
+\subsection{Insights}
+
+Based on the results from this experiment, it is clear that some methods are much faster than others.
+Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed.
+While KDE is a simple method, it quickly generates data that looks similar to the input data.
+DataSynthesizer in "Independent" mode is quick for a range of dataset sizes, but without configuration, it doesn't generate results that closely match the input dataset; e.g.
+the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes.
+
+In all cases, synthetic data generation is a CPU intensive task; no parallization has been implemented by either KFP nor the plugins used.
+While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 2GB for the Python process.
 

### 2018-06-11 sourcecode/python/kungfauxpandas.py
Saving updated tests, resolving some issues

@@ -126,8 +126,8 @@ class DataSynthesizerPlugin(PandaPlugin):
                 if self.verbose:
                     warnings.warn('Keyword argument', key, 'not used')
 
-        if self.num_tuples_to_generate is None and self.df_in is not None:
-            self.num_tuples_to_generate = len(self.df_in)
+        # for now, override tuples generated to be same as input dataframe
+        self.num_tuples_to_generate = len(self.df_in)
 
         # Below copied from example file
         self.description_file = './out/{}/description.txt'.format(self.mode)

### 2018-06-11 paper/long_version.tex
Auto Update from local Sharelatex

@@
   James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
-  Data Science to Patient Value (D2V), School of Medicine\\
-  University of Colorado Anschutz Medical Campus, Aurora, CO\\
+  Data Science to Patient Value (D2V)\\
+  School of Medicine\\
+  University of Colorado Anschutz Medical Campus\\
+  Aurora, CO\\
   \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
@@
 Despite the semantic differences, there is broad agreement that an independent experiment with confirmatory results is the strongest support of any experiment.
-One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
+One early influential paper on the topic of reproducibility in scientific computing lists the key factors in reproducibility as: available data, input parameters, documentation, software code, and an environment capable of running the provided software code.
 These items are difficult to completely convey in a traditional research paper \cite{schwab_making_2000}.
@@
 In this section we evaluate the performance of the KFP plugins to see how closely the methods meet the stated goals of ease of use, similarity to input data, and total time to run.
-Hardware for these performance and evaluation tests were from a 2017 MacBook Pro, 3.1 GHz Intel Core i7, 16GB 2133 MHz LPDDR3 with macOS 10.12.6.
-KFP software is written in Python 3.6; all packages and dependencies can be installed with identifical versions using the provided requirements.txt, environment.yml file, or Docker container.
+Hardware for these performance and evaluation tests was a 2017 MacBook Pro, 3.1 GHz Intel Core i7, 16GB 2133 MHz LPDDR3 with macOS 10.12.6.
+KFP software is written in Python 3.6; all packages and dependencies can be installed with identical versions using the provided requirements.txt, environment.yml file, or Docker container.
 Database queries were run against the relational database PostgreSQL version 9.6.9.
@@
 
-\subsection{Timing}
+\subsection{Timing Method}
 
 Table~\ref{timing_results} documents results obtained from running the various plugins.
-Source code for running performance tests are available in the Jupyter notebook performance\_tests.ipynb.
-The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct performance of the plugin class and function overloading mechanism as returns the input data frame unmodified.
-The KDE method is the custom developed method that acts as an example of how to create plugins.
+Source code for running these performance tests are available in the Jupyter notebook performance\_tests.ipynb.
+The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified.
+The KDE method is the custom method that acts as an example of how to create plugins.
 A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences.
-Independent mode generates synthetic data with each attribute being modeled independently from the others.
-Correlated attribute mode finds inter-column relationships to more accurately generate synthetic data.
-Both DataSynthesizer modes are run with no configuration and "w/Config" by passing in some column-wise dataset specific configuration.
+"Independent" mode generates synthetic data with each attribute being modeled independently from the others.
+"Correlated" attribute mode finds inter-column relationships to more accurately generate synthetic data.
+Both DataSynthesizer modes are run with no configuration and again "w/Config" by passing in some column-wise dataset specific configuration.
 
@@
 		\midrule 
-		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e-06 \\ 
+		Trivial & 2.5e-06 & 2.3e-06 & 2.3e-06 & 2.2e-06 & 2.2e-06 \\ 
 		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
+		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\ 
+		DS Independent w/Config & 0.045 & 0.040 & 0.064 & 0.120 & 0.799 \\
 		DS Correlated & 0.188 & 1.419 & 3.460 & 16.66 & 159.9 \\ 
-		DS Correlated w/Config & 0.172 & 0.627 & 1.393 & 342.7 &  \\ 
-		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\ 
-		DS Independent w/Config &  &  &  &  &  \\
+		DS Correlated w/Config & 0.172 & 0.627 & 1.393 & 342.7 & 2124 \\ 
 		\midrule
@@
 
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=120mm]{sample_source_data}
+  \caption{Sample of source data}
+  \label{fig:sample_source_data}
+\end{figure}
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=120mm]{sample_synthetic_data}
+  \caption{Sample of synthetic data}
+  \label{fig:sample_synthetic_data}
+\end{figure}
+
 \subsection{Insights}
 
-Based on the results from this experiment, it is clear that some methods are much faster than others.
+Figure~\ref{fig:sample_source_data} provides a few rows of the source data for the synthetic plugins.
+Figure~\ref{fig:sample_synthetic_data} provides a few rows of the synthetic data generated by DataSynthesizer in "Independent" mode.
+
 Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed.
-While KDE is a simple method, it quickly generates data that looks similar to the input data.
-DataSynthesizer in "Independent" mode is quick for a range of dataset sizes, but without configuration, it doesn't generate results that closely match the input dataset; e.g.
-the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes.
+As shown in the results, some methods are significantly faster than others as dataset size increases.
+Additionally, the other key constraint is having synthetic data be as close as possible to real data without reducing privacy.
+While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used.
+DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset.
+As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns.
+The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger dataset sizes.
 
-In all cases, synthetic data generation is a CPU intensive task; no parallization has been implemented by either KFP nor the plugins used.
+In all cases, synthetic data generation is a CPU intensive task; no parallelization has been implemented by either KFP nor the plugins used.
 While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 2GB for the Python process.
@@
 Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
-However, there are several areas that could be improved or researched further: improved code sharing, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
+Although one clear area for further research would be to develop plugins for additional faux-data methods, there are several areas that go beyond this simple step that could be researched further: improved code sharing of KFP, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
 
@@
 Finally, instead of taking the computational and labor intensive step of full EHR de-identification or synthesis, KFP takes the smaller and more easily implemented step of just-in-time data de-identification or synthesis.
+As shown in our experiments, if the proper method is selected, data can be quickly generated based on real data that the requester need not have direct access to.
 We surmise that this tool will improve data exploration and reduce dependency on complex processes required for data access.

### 2018-07-26 paper/amia.tex
Auto Update from local Sharelatex

--- 2018-06-11 paper/long_version.tex
@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2018
-
-% ready for submission
-%\usepackage{nips_2018}
-
-% to compile a preprint version, e.g., for submission to arXiv, add
-% add the [preprint] option:
-\usepackage[preprint]{nips_2018}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-%\usepackage[final]{nips_2018}
-
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2018}
+\documentclass{amia}
 
@@
 \usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing
-
 \usepackage{graphicx}       % added by seth - image support
@@
 \urlstyle{same}
+
+\begin{document}
+
 \title{%
@@
 \author{
-  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
-  Data Science to Patient Value (D2V)\\
-  School of Medicine\\
-  University of Colorado Anschutz Medical Campus\\
-  Aurora, CO\\
-  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
+  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett$^{1,2}$, MD, MS, Debashis Ghosh, PhD$^{1,3}$
   }
 
-\date{May 2018}
+\institutes{
+  $^1$CU Data Science to Patient Value (D2V), Anschutz Medical Campus, Aurora, CO;
+  $^2$Pediatric Critical Care, University of Colorado School of Medicine, Aurora, CO;
+  $^3$Biostatistics and Informatics, Colorado School of Public Health, Aurora, CO\\
+}
 
-\begin{document}
+\maketitle
 
@@
 
-\maketitle
+\noindent{\bf Abstract}
 
-\begin{abstract}
-There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data.
+\textit{There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data.
 Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility.
@@
 This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project.
-Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.
-\end{abstract}
+Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.}
 
@@
 
-\bibliographystyle{unsrt}
+\bibliographystyle{vancouver}
 

### 2018-07-26 paper/amia.tex
Auto Update from local Sharelatex

@@
 
-\textit{There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data.
+\textit{There are many barriers to data access and data sharing, especially in the domain of computational research on health care data.
 Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility.
@@
 Independent reproduction and replication of results are critical components of scientific inquiry.
-Barriers to data access and sharing are the most important impediments to reproducibility in machine learning (ML) research.
+Barriers to data access and sharing are the most important impediments to reproducibility in health data science research.
 Health care research has unique challenges because of necessary personal data privacy protections.
@@
 Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariable relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}).
-However, no pipeline currently exists with which ML investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing.
+However, no pipeline currently exists with which computational investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing.
 This work addresses that gap.
@@
 
-In the context of ML, sufficient detail is required such that an independent investigator could create the same hardware and software configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
+In the context of machine learning (ML), sufficient detail is required such that an independent investigator could create the same hardware and software configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly.
 Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
 
-Many domains in which ML investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data.
+Many domains in which health data science investigators work have legal barriers that make it difficult to enable independent verification of ML models which frequently require enormous amounts of training data.
 As an example, in the health care domain in the United States, a key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA).
@@
 
-Ideally a ML investigator should develop, test, and validate models using all available data.
+Ideally a computational investigator should develop, test, and validate models using all available data.
 This is most easily accomplished when they have unfettered access to all data in the problem domain they are working in.
@@
 
-KFP provides multiple methods by which a ML developer can access on-demand faux-data.
+KFP provides multiple methods by which a health data scientist can access on-demand faux-data.
 As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method.
@@
 
-KFP provides a unique contribution to the space of reproducible ML.
-Through providing ad-hoc faux-data, ML researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
+KFP provides a unique contribution to the space of reproducible computational research.
+Through providing ad-hoc faux-data, health data scientists can have lower barriers to accessing private data as well as reduced barriers to sharing faux-data derived from private data.
 Although one clear area for further research would be to develop plugins for additional faux-data methods, there are several areas that go beyond this simple step that could be researched further: improved code sharing of KFP, addressing institutional specific privacy issues, and evaluation of this system in a ML workflow.
 
-While we have provided software code and a description of our methods, we believe that ML reproducibility should go beyond just making source code available.
+While we have provided software code and a description of our methods, we believe that computational reproducibility should go beyond just making source code available.
 Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}.
-This is a level of code sharing rarely achieved in ML research.
+This is a level of code sharing rarely achieved in computation based research.
 Currently there is no standard long term format that works for all computational environments.
@@
 
-The last area recommended for further research is to deploy and observe the use of KFP in an active ML environment where researchers are working with sensitive datasets.
+The last area recommended for further research is to deploy and observe the use of KFP in an active health data science environment where researchers are working with sensitive datasets.
 A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
@@
 We surmise that this tool will improve data exploration and reduce dependency on complex processes required for data access.
-The result of this system will be improved reproducibility in ML.
+The result of this system will be improved reproducibility in health data science.
 

### 2018-07-27 paper/amia.tex
Auto Update from local Sharelatex

@@
 \author{
-  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett$^{1,2}$, MD, MS, Debashis Ghosh, PhD$^{1,3}$
+  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett, MD, MS$^{1,2}$,\\ Debashis Ghosh, PhD$^{1,3}$
   }
@@
 As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method.
-Data can either be viewed directly in browser or downloaded in csv format for use in a ML process.
+The SPA additionally allows for the upload of csv files (not shown) to allow for ease of evaluation and testing of the provided data synthesis methods.
+Faux-data can either be viewed directly in browser or downloaded in csv format for use in a ML process.
 Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query.

### 2018-07-27 paper/amia.tex
Auto Update from local Sharelatex

@@
     urlcolor=blue,
+    citecolor=blue
 }
@@
 
-\textit{There are many barriers to data access and data sharing, especially in the domain of computational research on health care data.
+\textit{There are many barriers to data access and data sharing, especially in the domain of computational research using health care data.
 Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility.
@@
 As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability.
-To further the aim of reproducibility we have provided our code and a sample of a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
+To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
 

### 2018-07-30 paper/amia.tex
Auto Update from local Sharelatex

@@
 \graphicspath{ {./images/} }
+\usepackage{footmisc}       % better footnote support
 
@@
 
+\renewcommand{\thefootnote}{\alph{footnote}}
+
 \begin{document}
@@
 \author{
-  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett, MD, MS$^{1,2}$,\\ Debashis Ghosh, PhD$^{1,3}$
+  James King MIDS$^{1}$\footnote{Authors JK and SR contributed equally to this work\label{contribution}},
+  Seth Russell MS$^{1}$\footref{contribution},
+  Tellen D. Bennett, MD, MS$^{1,2}$,\\
+  Debashis Ghosh, PhD$^{1,3}$
   }
@@
 \maketitle
-
-% Advice from Tell:  articulate the problem with evidence (i.e. papers)
-%   Enable reproducibility - patient value, make process of replication easier
-%   Time saving
-%   legal risk (carrying data in laptops, etc)
-%   Multiple comparison?
-%   Educational data sets
-%  Definition of :reproducibility 
-%       reproducibilty - everything same - code, data, result
-%       replicability - code same, new data, same result find Peng & Leek reference (also look at blog)
-%   unit testing...
-%   Proof of privacy guarantees?
 
@@
 Next the processed query is executed against the protected data set and results are passed into the modular synthesis process.
-While the current implementation only utilizes a couple of synthesis methods, ML developers or data warehouse owners can insert their own custom method or modify existing methods.
+While the current implementation only utilizes a couple of synthesis methods, data scientists or data warehouse owners can insert their own custom method or modify existing methods.
 Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
@@
 The SPA additionally allows for the upload of csv files (not shown) to allow for ease of evaluation and testing of the provided data synthesis methods.
-Faux-data can either be viewed directly in browser or downloaded in csv format for use in a ML process.
+Faux-data can either be viewed directly in browser or downloaded in csv format for use in a health data science process.
 Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
@@
 \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
-As a result of their methods, the DataSynthezier offers a unique contribution to the space: it can work with no configuration other than input data, or can be configured to provide more custom results.
+As a result of their methods, the DataSynthezier offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results.
 In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
@@
 As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns.
-The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger dataset sizes.
+The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger input dataset sizes.
 
@@
 In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009} as the key method for privacy protection.
-However, it is not clear that these methods are appropriate for use in ML in general or domains other than education.
+However, it is not clear that these methods are appropriate for general use in ML or domains other than education.
 Thus, in this work, no attempt has been made to constrain data set sizes nor provide additional proofs of data protection.
@@
 
-The last area recommended for further research is to deploy and observe the use of KFP in an active health data science environment where researchers are working with sensitive datasets.
+The last area recommended for further research is to deploy and observe the use of KFP in an active health data environment where researchers are working with sensitive datasets.
 A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store.
 Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
-% include some of this? 
-% Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al.
-\cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.
-In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard.
-Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
 

### 2018-07-30 paper/amia.tex
Auto Update from local Sharelatex

@@
 
-Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariable relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}).
+Several methods exist to de-identify (remove key identifiers, group individuals, and related anonymization techniques \cite{hippapro}) and synthesize data (create data through algorithmic means, population level statistics, randomization, ideally with preservation of multivariate relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}).
 However, no pipeline currently exists with which computational investigators can routinely \emph{anonymize} or \emph{synthesize} data to facilitate access and sharing.
@@
 To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
+Also included in our GitHub repository are unit tests for KFP using the Python library pytest.
+Unit tests helped to validate correct functioning of KFP and provides a foundation from which to prevent regressions as new features are added.
 

### 2018-07-31 paper/amia.tex
Auto Update from local Sharelatex

@@
 The current legal environment creates a difficult situation for scientists in the health care domain.
-Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}.
+Early examples of re-identification attacks \cite{sweeney_2002} have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}.
 Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}.
@@
 \end{figure}
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=120mm]{data_synthesis_process}
-  \caption{Data synthesis process.}
-  \label{fig:synthesis_process}
-\end{figure}
 
@@
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=120mm]{data_synthesis_process}
+  \caption{Data synthesis process.}
+  \label{fig:synthesis_process}
+\end{figure}
 
@@
 As shown in the results, some methods are significantly faster than others as dataset size increases.
-Additionally, the other key constraint is having synthetic data be as close as possible to real data without reducing privacy.
+Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy.
 While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used.

### 2018-08-21 paper/amia.tex

@@
 \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data.
-As a result of their methods, the DataSynthezier offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results.
+As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results.
 In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

### 2018-11-02 paper/amia.tex
Auto Update from local Sharelatex

@@
 Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand.
+Items in blue are features of KFP; items in grey or with dashed lines are not provided.
+KFP is designed to fit into an existing infrastructure with a protected data source secured behind a firewall along with user authentication.
 
@@
 Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process.
+Items in grey with dashed lines are not provided by KFP but are either pre-existing or provided by the user.
 All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process.
@@
 While the current implementation only utilizes a couple of synthesis methods, data scientists or data warehouse owners can insert their own custom method or modify existing methods.
-Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
+For additional details on the modular synthesis processes, see the section "Included Synthesis Methods." Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user.
 Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.
@@
 KFP provides a framework by which any number of methods for data privacy can be carried out.
-For demonstration purposes we have implemented two plugins that use different techniques for data synthesis.
+This framework is comprised of a provided base class, several examples of plugins, and unit tests for validation purposes.
+As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer.
 The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware.

### 2018-11-02 sourcecode/python/notebooks/Tutorials/KFP-Dem.Rmd

---
title: "Forever Monstrous"
author: "James King"
date: "8/30/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Forever Monsterous
## A Kung Faux Pandas Tutorial

Kung Faux Pandas (KFP) is a set of tools which extends the [Pandas](https://pandas.pydata.org/ "Pandas Homepage") dataframe to include some tools for generating synthetic data.

There are many reasons to create synthetic data, but KFP assumes the reason is to give a statistical analyst "realistic" data, which we term _faux_ data, without exposing the real dataset.   
Details on the tools and how to install them are available on the [KFP github repository] (https://github.com/CUD2V/kungfauxpandas).

This tutorial assumes you have installed KFP as well as some standard data science tools, such as numpy, scipy, and matplotlib.

## Chapter 1:  The Problem
Monsters are a tricky lot.   They have widely varying statistics and capabilities and many have spent centuries building up their reputations in order to disuade adventurers from invading their spaces.  The smarter varieties of monsters have retained good lawyers through the ages, and it in most jurisdictions it's actually illegal to publish the "personal" data on any monster.

Of course, we would like to study the monsters without violating their privacy rights.   KFP can help this problem!

1. Generate a fake data set based on the real stuff
2. Work out all steps necessary to clean the data up
3. Code the data cleaning steps into a function
4. Re-run the data generation using the data cleaner
5. Get a clean, synthetic data set to study
6. Have a trusted agent (DM?) run your study code on the real data and deliver you the results.

# Step 0:  Get the Real Data!
In the real scenario, this step would be done in a secure computing environment to which the researcher has no access.  In order to facilitate the tutorial, we're including this step.

# Data File Available [Here](https://docs.google.com/spreadsheets/d/16ajgJpvUI0wYcSU7kjHutw8oB6Zv6eIAo5JtI6PLvu8/edit#gid=776794522)

```{python include=FALSE} 
import sqlite3
import pandas as pd
import numpy as np
import scipy as sp
import scipy.stats as stats
import pylab as plt
from collections import Counter
import datetime
import sys
sys.path.append('../')
sys.path.append('../../../plugins/DataSynthesizer/DataSynthesizer/')
sys.path.append('../../../plugins/DataSynthesizer/')
from importlib import reload
from kungfauxpandas import KungFauxPandas, TrivialPlugin, DataSynthesizerPlugin, KDEPlugin
from fractions import Fraction

monsterfile = "../../../data/D&D 5e Monster List with Ability Scores.xlsx - Monsters by Ability Score.csv"
```

```{python, include=TRUE}
df = pd.read_csv(monsterfile)
df.sample(10)
```

```{python pyplot, echo=FALSE}
pass
#fig.savefig("pyplot.png")
#plt.close(fig)
```
```{r, echo=FALSE}
knitr::include_graphics("pyplot.png")
```

### 2018-11-02 paper/amia.tex
Auto Update from local Sharelatex

@@
 As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability.
-To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
+To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker \cite{merkel_docker, docker_website} container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
 Also included in our GitHub repository are unit tests for KFP using the Python library pytest.
@@
 Faux-data can either be viewed directly in browser or downloaded in csv format for use in a health data science process.
-Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
 In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section.
+The provided Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query.
 Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
+This Python native API gives full control over all parameters specific each synthesis plugin; the SPA and REST APIs use the default parameters associated with each plugin.
 
@@
 KFP provides a framework by which any number of methods for data privacy can be carried out.
-This framework is comprised of a provided base class, several examples of plugins, and unit tests for validation purposes.
+This framework is comprised of a some base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes.
 As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer.
-The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware.
+The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles ordinal and ratio data yet runs quickly on standard consumer level hardware.
+Two methods for this plugin are provided: an independent attribute mode where each variable is considered in isolation, and a correlated attribute mode where all variables are evaluated and synthesized together on an observation by observation basis.
 The DataSynthesizer method, created by Ping et al.
@@
 In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
+
+some text \\ and some more text \\ test
+
+\begin{table}
+   \caption{Included Data Synthesis Methods}
+   \label{included-methods}
+   \centering
+   \begin{tabular}{p{12em} l p{20em}}
+     \toprule
+     Method                                 & Source                    & Notes \\
+     \midrule
+     Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
+     DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
+     \bottomrule
+   \end{tabular}
+ \end{table}
 
@@
 As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns.
-The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger input dataset sizes.
+The DataSynthesizer "Correlated" attribute mode generates more realistic synthetic data than the "Independent" mode as variables in a single observation that are correlated are modeled together.
+The "Correlated" method does have a significant larger computational burden when generating synthetic data from larger input dataset sizes.
 

### 2018-11-07 paper/amia.tex
Auto Update from local Sharelatex

@@
 \begin{table}
-   \caption{Included Data Synthesis Methods}
+   \caption{Summary of Included Data Synthesis Methods}
    \label{included-methods}
@@
      \midrule
-     Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
-     DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
+     %row 1 column 1
+     Kernel Density Estimator; independent attribute mode
+     %row 1 column 2
+     & scipy.stats.gaussian\_kde
+     %row 1 column 3
+     & Creates a Gaussian Kernel Density Estimator using the Silverman method; fast but doesn’t maintain correlation between variables of the same observation.\\
+     %row 2 column 1
+     Kernel Density Estimator; corelated attribute mode
+     %row 2 column 2
+     & scipy.stats.gaussian\_kde
+     %row 2 column 3
+     & Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01\\
+     %row 3 column 1
+     DataSynthesizer; independent attribute mode
+     %row 3 column 2
+     & Ping et al.
+     %row 3 column 3
+     & A histogram is derived for each attribute, noise is added to the histogram to achieve differential privacy, and then samples are drawn for each attribute; fast but doesn’t maintain correlation between variables of the same observation.\\
+     %row 4 column 1
+     DataSynthesizer; correlated attribute mode
+     %row 4 column 2
+     & Ping et al.
+     %row 4 column 3
+     & Data is generated through a differentially private Bayesian network capturing the correlation between attributes.
+Computationally expensive and requires larger input dataset compared to independent attribute mode.\\
      \bottomrule
@@
 In all cases, synthetic data generation is a CPU intensive task; no parallelization has been implemented by either KFP nor the plugins used.
-While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 2GB for the Python process.
+While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 4.7GB for the Python process.
 

### 2018-11-07 paper/amia.tex
Auto Update from local Sharelatex

@@
      %row 2 column 1
-     Kernel Density Estimator; corelated attribute mode
+     Kernel Density Estimator; correlated attribute mode &
      %row 2 column 2
-     & scipy.stats.gaussian\_kde
+     scipy.stats.gaussian\_kde &
      %row 2 column 3
-     & Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01\\
+     Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01 \\
      %row 3 column 1
@@
 The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified.
-The KDE method is the custom method that acts as an example of how to create plugins.
+The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins.
 A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences.

### 2018-11-08 sourcecode/python/kungfauxpandas.py
Updating notebook to include new correlated attribute mode for KDE plugin

@@ -326,7 +326,7 @@ class KDEPlugin(PandaPlugin):
         df_num = pd.DataFrame(out_df).dropna()
 
         # Build KDE & resample
-        if verbose:
+        if self.verbose:
             print('Building KDE Covariate Model')
 
         # For unobvious reasons, inputs to the gaussian_kde

### 2018-11-08 paper/amia.tex
Auto Update from local Sharelatex

@@
 
-some text \\ and some more text \\ test
-
 \begin{table}
@@
    \end{tabular}
+   \vspace{+3mm}
  \end{table}
@@
 The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins.
+Additionally the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data.
 A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences.
@@
 		Trivial & 2.5e-06 & 2.3e-06 & 2.3e-06 & 2.2e-06 & 2.2e-06 \\
-		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
+		KDE Independent & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\
+		KDE Correlated & 0.017 & 0.021 & 0.027 & 2.43 & 120.8 \\
 		DS Independent & 0.044 & 0.050 & 0.103 & 0.268 & 2.608 \\
@@
 	\end{tabular}
+	\vspace{-4mm}
 \end{table}

### 2018-11-19 paper/amia.tex
Auto Update from local Sharelatex

@@
 as if it were the actual source data.
-KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model.
-Two of these plug-ins are provided with full documentation for creating other plug-ins.
+KFP provides a standard mechanism for wrapping a privacy protection method into a plugin which integrates the method with the Pandas DataFrame model.
+Two of these plugins are provided with full documentation for creating other plugins.
 
@@
 By focusing on just the data needed, performance is improved, the need for extensive modeling or metadata configuration is reduced, and the amount of faux-data generated and stored is minimized.
-Although the plugable methods included for faux-data generation have been shown to effectively replace source data for analysis, KFP facilitates a more through process that includes an initial exploration with faux-data followed by a repetition of methods on original source data through query logging and thereby aiding in replication.
+Although the plugin methods included for faux-data generation have been shown to effectively replace source data for analysis, KFP facilitates a more through process that includes an initial exploration with faux-data followed by a repetition of methods on original source data through query logging and thereby aiding in replication.
 
@@
 KFP provides a framework by which any number of methods for data privacy can be carried out.
-This framework is comprised of a some base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes.
+This framework is comprised of base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes.
 As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer.
@@
 The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins.
-Additionally the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data.
+Additionally, the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data.
 A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences.
@@
 DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset.
-As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns.
+As an example, the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns.
 The DataSynthesizer "Correlated" attribute mode generates more realistic synthetic data than the "Independent" mode as variables in a single observation that are correlated are modeled together.
@@
 KFP removes barriers to data access and data sharing via self-service faux-data generation.
-Users of KFP do not need to have access to a protected dataset nor does a human have to be involved in translating researchers data needs into a non-protected dataset.
+Users of KFP do not need to have access to a protected dataset nor does a human have to be involved in translating researcher's data needs into a non-protected dataset.
 This self-service data can be differentially private or meet other privacy needs based on plugin capabilities.
